\hline
\multicolumn{1}{|c|}{\textbf{Sand beach, South Africa}, $\rho = 0.369615$} \\
\hline
Gastrosaccus, Callianassa, Donax; bacteria; Cumacea; Turbellaria; Nemertea; Bathyporeia; Bullia; Ovalipes; Talorchestia; sedentary polychaeta; errant polychaete; isopods; Larus nematode worms; protozoa; nematode; Curlew sandpiper; Sanderling; elasmobranch fishes; predatory fishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sítios Novos reservoir (2011)}, $\rho = 0.335623$} \\
\hline
Camarão; Cladocera; Copepoda; M. tuberculata; Ostracoda; Outros Invertebrados; Rotifera; Insecta; P.brevis; O.niloticus juvenil; O.niloticus adulto; L.piau; Other Birds; Caracara plancus; Poecilia; A. gigas 1; A.brasiliensis juvenil; Cichla sp. juvenil; A.bimaculatus; Pescada; A.brasiliensis adulto; Cichla sp. adulto; Phytoplankton; A. gigas 3; A. gigas 4; A.gigas 2; Ardea alba; Egretta thula; Phalacrocorax brasilianus; Butorides Striata\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Terminos Lagoon (1980)}, $\rho = 0.321184$} \\
\hline
Meiofauna; Polychaetes; Zooplankton; Microcrustaceans; Molluscs; Sparidae; Other macroinvertebrates; Penaeids; Brachyurans; Tetraodontidae; Engraulidae; Ariidae; Gerreidae; Haemulidae; Other fish; Scianidae; Benthic autotrophs; Phytoplankton; Lutjanidae\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Huizache-Caimanero (1984)}, $\rho = 0.305621$} \\
\hline
Gastropods; Polychaets; Microcrustaceans; Chanids; Zooplankton; Bivalvs; Penaeids; Palaemonids; Mugilids; Gobioidei; Clupeidei; Gerreids; Callinectes; Pleuronectoidei; Haemulids; Ariids; Centropomids; Carangids; Lutjanids; Elopids; Sciaenids; Macrophytes; Poeciliids; Phytoplankton; Belonoidei\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern Gulf of Mexico (2005)}, $\rho = 0.303594$} \\
\hline
SEP; INF; ZOO; MEP; MUL; MEN; SHP; CPH; ReO; CoO; BUT; ASK; GTR; DCIF; SHS; BCIF; ReIF; BeP; SRF; CRB; ST; CoP; BGR3; YEG3; OSN; VSN; RAY; MSN; TLF; RD; BGR0; ReP; TUR; YEG1; RSN6; GGR0; RGR0; RGR1; RGR3; SBD; OcP; SWG; GOL; RSN0; GGR3; SCS; ASN; PCP; AMB; DWG; SNB; SM3; BFT; DOL; COB; KM3; BIL; TUN; SWO; LCS; YFT; BKT; DUS; LOS; BGR1; OPL; YEG0; SGR; GGR1; PHY; ALG; LOP; SM0; KM0\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Gulf of California (1990)}, $\rho = 0.299334$} \\
\hline
Zooplankton; Farfantepenaeus californiensis (ADULTS); Benthic inv.; Litopenaeus stylirostris (ADULTS); Stomatopoda; Polychaeta; Callinectes sp.; Mojarras; Myctophidos; Flat fishes; Cephalopoda; Farfantepenaeus californiensis (JUVENILES); Litopenaeus stylirostris (JUVENILES); Sicyonia penicillata; Other fishes; Sciaenidae; Haemulidae; Elasmobranchi (SHARKS); Totoaba macdonaldi (ADULTS); Elasmobranchi (RAYS); Serranidae; Rhinobatidae; Small pelagics; Odontoceti; Merluccidae; Totoaba macdonaldi (JUVENILES); Macrophytes; Phytoplankton; Coastal birds; Mysticeti; Phocoena sinus; Marine birds; Zalophus californianus\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{West coast of Sabah (1972)}, $\rho = 0.298921$} \\
\hline
Zooplankton; Meiobenthos; Macrobenthos; Small crsustaceans; Octopus sepia; Shrimps; Crabs Lobsters; Squids; Engraulids Clupeids; Mullids; Small pelagics; Lactarids; Leiognathids; Balistids; Demersal zoobenthos feeders; Nemipterids; Reef associated fish; Large zoobenthos feeders; Sciaenids; Flatfishes Soles; Intermediate predators; Carangids; Macrobenthic flora; Phytoplankton; Lutjanids; Serranids; Tuna; Large predators\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Barra Del Chuy (1992)}, $\rho = 0.298553$} \\
\hline
Birds; Atlantorchestoidea brasiliensis; Carabide; Euzonus furciferus; Excirolana armata; Excirolana braziliensis; Macrochiridiotea giambiagiae; Phoxocephalopsis sp.; Scolelepis gaucha; Donax hanleyanus; Emerita brasiliensis; Mesodesma mactroides; Zooplankton; Hemipodus olivieri; Buccinanops duartei; Phytoplankton; Olivella formicacorsii; Fishes; Olivancillaria vesica auricularia\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Tropical plankton community, Pacific}, $\rho = 0.293951$} \\
\hline
bacteria; Appendicularia large; Radiolaria; Acartia  large; Infusoria; copepodites; nauplii; Appendicularia small; Oithona-Oncaea large; Calanus small; Acartia small; Amphipoda; Euchaeta; Euphausia; Calanus large; Centropages; Medusae; Oithona-Oncaea small; small-size phytoplankton; medium-size phytoplankton; large-size phytoplankton; Chaetognatha\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sørfjord (1993)}, $\rho = 0.292600$} \\
\hline
small zooplankton; detrivore echinoderms; detrivore polychaetes; large bivalves; other benthic invert; other large zooplantkon; euphausiids; small molluscs; small benthic crustaceans; shrimps; predatory benthos; large decapoda; schypomedusae; small king crab; large cod; large other fish; small cod; small other fish; mammals; phytoplankton; Large King crab; chaetognaths; herring; Cormorants\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Malangen Fjord (2017)}, $\rho = 0.290582$} \\
\hline
Bacteria; Microzooplankton; Detritivore polychaetes; Sea cucumbers; Small krill; Benthic detritivore echinoderms; Hagfish; Other benthic detritivore invertebrates; Meiofauna; Suprabenthos; Macro mesozooplankton; Large krill; Heterotrophic nanofl.; Benthopelagic shrimps; Witch flounder; Predatory invertebrates; Redfishes; Pelagic shrimps; Mesopelagic fishes; Rabbit fish; Other commercial demersal fishes; Benthopelagic cephalopods; Marine mammals; Jellyfish and ctenophores; Pouts; Greater argentine; Large phytoplankton; Blue whiting; Rays and skates; Seabirds; Velvet belly; Large fish feeders\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bamboung (2003)}, $\rho = 0.290392$} \\
\hline
Macrobenthos; Tilapias; Zooplancton; Meiobenthos; Petits benthoph; Crevettes; Ethmalose; Mulets; Crabes; Sardinelle +; Gerres; Mâchoirons mari; Pomadasys; Diagramme +; Raies; Pompaneau +; Carangues; Requins; Grand capitaine; Barracudas +; Oiseaux; Dauphins; Otolithes +; Breton africain; Microphytobenth; Phytoplancton; Sole-langue +; Vivaneaux +; Tétrodon +; Elops\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bamboung (2006)}, $\rho = 0.290392$} \\
\hline
Macrobenthos; Tilapias; Zooplancton; Meiobenthos; Petits benthoph; Crevettes; Ethmalose; Mulets; Crabes; Sardinelle +; Gerres; Mâchoirons mari; Diagramme +; Pomadasys; Raies; Pompaneau +; Carangues; Requins; Grand capitaine; Barracudas +; Oiseaux; Dauphins; Otolithes +; Breton africain; Microphytobenth; Phytoplancton; Sole-langue +; Vivaneaux +; Tétrodon +; Elops\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sirinhaém River (2013)}, $\rho = 0.285667$} \\
\hline
Zooplakton; Bivalves; Gastropods; Fiddler crabs; Mullet  ; Polychaetas; Croaker; Shrimp ; Blue crab ; Mojarra(Diapterus spp); Puffer; Pemecou sea catfish; Others Catfish; Mojarra(Eucinostomus spp); Flatfish; Drum ; Snapper; Snook; Grunt; jack; Phythoplankton; Epiphyton; Microphytobenthos ; Sardines\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Central Gulf of California (1978)}, $\rho = 0.285322$} \\
\hline
Zooplankton; Shrimp; Meiobenthos; Stomatopods; Polychaeta; Crabs; Red crab; Paralichthydae; Myctophidae; Other macrocrus; Other fish; Lutjanidae; Haemulidae; Serranidae; Sciaenidae; Scombridae; Carangidae; Clupaeidae; Sharks / Rays; Squid; Sea birds; Phytoplankton; Other molluscs; Scorp/Triglidae; Sea mammals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Deep Western Mediterranean sea (2009)}, $\rho = 0.284998$} \\
\hline
Mesopelagic crustacea; Meiobenthos; Benthic invertebrates, other; Benthic invertebrates, crustacea; Aristeus antennatus; Macrourids; Other demersal, small; Lepidion lepidion; Mora moro; Benthopelagic fish; Phycis blennoides; Alepocephalus rostratus; Monkfish; Cephalopods; Zooplankton, BBL; Surface production; Demersal sharks; Zooplankton, gelatinous; Bluntnose sixgill shark\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Jalisco and Colima Coast (1995)}, $\rho = 0.284357$} \\
\hline
Otros peces; Braquiuros; Infauna; Equinodermos; Otros macroinve; Moluscos; Estomatópodos; Peneidos; Otros crustáceo; Otros lutjánido; Pulpo; Pleuronéctidos; Rayas; Ophidiidos; Gerreidos; Tetraodóntidos; Haemúlidos; Sciánidos; Serranidos; Carángidos; Escómbridos; Anguilas y more; Adultos Lutjanu; Dorado; Juveniles Lutja; Tiburones; Zooplancton; Sardinas; Mamíferos marin; Aves marinas; Synodontidos; Tortugas marina; Sierra; Gasterosteidos; Fitoplancton; Picudos\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Contemporary Alosine (2000)}, $\rho = 0.281390$} \\
\hline
Bacteria; Small Copepods; Megabenthos filters; Microzooplankton; Large Copepods; Macrobenthos mollusks; Macrobenthos polychaete; Macrobenthos others; Small Atlantic menhaden; Macrobenthos crustaceans; Medium Atlantic menhaden; Micronekton; Large Atlantic menhaden; Shrimp; Gelatinous Zooplankton; Megabenthos others; Small pelagics; Atlantic herring; Mesopelagic; Alosines; Baleen whales; Butterfish; Anchovies; Squid; Demersal piscivores - other; Demersal omnivores - other; Hake; Sharks - pelagic; Small dogfish; Large dogfish; Demersal benthivores - other; Small weakfish ; Large cod; Large summer  flounder; Medium bluefish; Skate; Sharks - coastal; Mackerel; Croaker; Medium cod; Small bluefish; Haddock; Small cod; Small summer  flounder; Small yellowtail flounder; Small striped bass; Medium weakfish; Medium striped bass; Odontocetes; Phytoplankton; Large yellowtail flounder; Large striped bass; Seabird; Large pelagics (HMS); Large weakfish; Pinnipeds; Medium pelagic - other; Large bluefish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North South of China Sea (1970)}, $\rho = 0.276372$} \\
\hline
Zooplanktons; Polychaetes; Non-ceph molluscs; Benthic crustaceans; Shrimps; Echinoderms; Crabs; Sessile/other invertebrates; Pelagic fish (less than 30cm); Benthopelagic fish; Juvenile large pelagic fish; Seaturtles; Demesral fish (less than 30 cm); Juv demersal fish (30+cm); Cephalopods; Lizard fish (Synodontids); Pelagic fish (30+cm); Melon seed; Adult demersal fish (30+cm); Threadfin bream (Nemipterids); Seabirds; Croakers (30+cm); Pelagic sharks and rays; Croakers (less than 30cm); Other mammals; Juv large croakers; Demersal sharks and rays; Jellyfish; Adult groupers; Juv Hairtail (Trichiurids); Phytoplanktons; Bigeyes (Priacanthids); Adult hairtail (Trichiurids); Benthic producers; Pomfret (Stromateids); Snappers; Pinnipeds\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Restored Alosine Biomass (2000)}, $\rho = 0.275154$} \\
\hline
Bacteria; Copepods\_S; Megabenthos\_filters; Microzooplankton; Copepods\_L; Macrobenthos\_mollusks; Macrobenthos\_polychaete; Macrobenthos\_others; Atlantic\_menhaden\_S; Macrobenthos\_crustaceans; Micronekton; Atlantic\_menhaden\_M; Atlantic\_menhaden\_L; Shrimp; Megabenthos\_others; Small\_pelagics; Gelatinous\_Zooplankton; Atlantic\_herring; Anchovies; Squid; Butterfish; Mesopelagic; Demersal\_piscivores; Demersal\_omnivores; Hake; Baleen\_whales; Sharks\_pelagic; Dogfish\_S; Dogfish\_L; Demersal\_benthivores; Weakfish\_S ; Cod\_L; Anadromous\_alosines; Summer\_flounder\_L; Bluefish\_M; Skate; Sharks\_coastal; Mackerel; Croaker; Cod\_M; Bluefish\_S; Haddock; Cod\_S; Summer\_flounder\_S; Yellowtail\_flounder\_S; Striped\_bass\_S; Weakfish\_M; Striped\_bass\_M; Odontocetes; Phytoplankton; Yellowtail\_flounder\_L; Weakfish\_L; Striped\_bass\_L; Large\_pelagics\_HMS; Seabird; Pinnipeds; Medium\_pelagic; Bluefish\_L\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Central Atlantic (1990)}, $\rho = 0.272142$} \\
\hline
Sm. Zoop. shlw; Het. bacteria; Sm. Zoop. deep; Megabenthos; Meiobenthos; Macrobenthos; Lg. Bathyd. abs; Lg. Zoop. deep; Lg. Bathyp. fish; Sm. Bathyp. fish; Sm. Epi. fish; Sm. Meso fish; Md. Bathyp.fish; Md. Epi. fish; Sm. Bathyd. slp; Sm. Bathyd. abs; Lg. Bathyd. slp; Seabirds; Pelagic sharks; Sm Squids; Lg. Epi. fish; Lg. Zoop. shlw; Toothed whales; Benth. ceph.; Skipjack; Lg Squids; Phytoplankton; Lg. Meso fish; Baleen whales; Lg. Plank. fish; Bluefin; Bigeye; Yellowfin; Albacore; Swordfish; Beaked whales; Billfishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Central Atlantic (1950)}, $\rho = 0.271786$} \\
\hline
Sm. Zoop. shlw; Het. bacteria; Sm. Zoop. deep; Megabenthos; Meiobenthos; Macrobenthos; Lg. Bathyd. abs; Lg. Zoop. deep; Lg. Bathyp. fish; Sm. Bathyp. fish; Sm. Epi. fish; Sm. Meso fish; Md. Bathyp.fish; Md. Epi. fish; Sm. Bathyd. slp; Sm. Bathyd. abs; Lg. Bathyd. slp; Seabirds; Pelagic sharks; Sm Squids; Lg. Epi. fish; Lg. Zoop. shlw; Toothed whales; Benth. ceph.; Skipjack; Lg Squids; Phytoplankton; Lg. Meso fish; Baleen whales; Lg. Plank. fish; Bluefin; Bigeye; Yellowfin; Albacore; Swordfish; Beaked whales; Billfishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Atlantic (1950)}, $\rho = 0.271674$} \\
\hline
Sm. Zoop. shlw; Het. bacteria; Sm. Zoop. deep; Megabenthos; Meiobenthos; Macrobenthos; Lg. Bathyd. abs; Lg. Zoop. deep; Lg. Bathyp. fish; Sm. Bathyp. fish; Sm. Epi. fish; Sm. Meso fish; Md. Bathyp.fish; Md. Epi. fish; Sm. Bathyd. slp; Sm. Bathyd. abs; Lg. Bathyd. slp; Seabirds; Pelagic sharks; Sm Squids; Lg. Zoop. shlw; Lg. Epi. fish; Toothed whales; Benth. ceph.; Lg Squids; Skipjack; Phytoplankton; Lg. Meso fish; Baleen whales; Lg. Plank. fish; Bluefin; Bigeye; Yellowfin; Albacore; Beaked whales; Swordfish; Billfishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Atlantic (1997)}, $\rho = 0.271674$} \\
\hline
Sm. Zoop. shlw; Het. bacteria; Sm. Zoop. deep; Megabenthos; Meiobenthos; Macrobenthos; Lg. Bathyd. abs; Lg. Zoop. deep; Lg. Bathyp. fish; Sm. Bathyp. fish; Sm. Epi. fish; Sm. Meso fish; Md. Bathyp.fish; Md. Epi. fish; Sm. Bathyd. slp; Sm. Bathyd. abs; Lg. Bathyd. slp; Seabirds; Pelagic sharks; Sm Squids; Lg. Zoop. shlw; Lg. Epi. fish; Toothed whales; Benth. ceph.; Skipjack; Lg Squids; Phytoplankton; Lg. Meso fish; Baleen whales; Lg. Plank. fish; Bluefin; Bigeye; Yellowfin; Albacore; Swordfish; Beaked whales; Billfishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Lake Pyhajarvi, littoral zone, Finland}, $\rho = 0.270052$} \\
\hline
Cyclopoida; Keratella, Kellicottia; Codonella, Vorticella; Lymnaea; chironomids; Pisidium; Stylodrilus; Ephemera; Nematoda; Asellus; Erpobdella; Ablabesmyia; Polycentropus; Coregonus albula; Coregonus lavaretus; Sida, Eurycercus; Daphnia, Bosmina; young fish; phytoplankton; aquatic plants; Rutilus rutilus; Gymnocephalus cemus; Perea fluviatilis\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Alto Golfo de California}, $\rho = 0.268430$} \\
\hline
Infauna; Mojarras; Haemulidos; Poliquetos; Myctophidos; Cefalópodos; C. azul; C. cafe; Otros peces; C. de roca; Stomatópodos; Peces planos; Mantarayas; Serranidos; Rhinobatidos; Sciaenidos; Zooplancton; Pelágicos; Ballenas dentadas; Tiburón; Totoaba; Jaibas; Merlucciidos; Fitoplancton; Macrofitas; Ballenas barbadas; Lobo marino; Vaquita\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Guinea  (2004)}, $\rho = 0.267419$} \\
\hline
Large zooplankton; Small zooplankton; Benthos; Crustacea; Cephalopods; Mullets+; Sardinella+; Horse mackerels+; ML demersal invert.eaters; S. demersal invert.eaters; Seabream+; SM demersal pred.eaters; Bobo croaker; Grunts+; Sea catfish; Sharks+; Sea birds; Barracudas+; Carangids; L. demersal pred.eaters; Large pelagics; Other croakers; Ethmalosa; Rays+; Dolphins; Bathy-dem pred.eaters; Primary producers; Giant Afr. threadfin; Bathy-dem invert.eaters; Turtles; Soles+; Lesser Afr. threadfin; Royal threadfin; Whales\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Port Cros (1998)}, $\rho = 0.265184$} \\
\hline
Foraminifera; Brittle stars +; Sea cucumbers; Small zooplankton; Bivalves; Small crustaceans; Sea urchins; Gorgonians; Amphipods; Gastropods; Mullets; Suspensivores; Sea worms; Crabs; Decapods; Cephalopods; Stripped red mulet +; Sea stars; Large zooplankton; Horse mackerels and sand smelts +; Wrasses; Blennies +; Gobies; Pipefishes +; Scorpionfishes and combers +; Large-scaled scorpionfish +; Amberjack and dentex +; Posidonia; Shallow seaweeds; Salema - adults; Salema - juveniles; Diplodus +; Pagellus; Deep seaweeds; Phytoplankton; Dusky grouper - small; Seabirds; Dusky grouper - medium; Dusky grouper - large; Rays\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Virgin Islands (1960)}, $\rho = 0.263946$} \\
\hline
I7 Decom/Microf; F9 ReefherbBG; F8 ReefherbSM; I5 Sess.Animals; I3 Crustacea; I4 Worm/Mollusc; I2 Echinoderms; F6 ReefomniSM; F1 Sharks/Rays; F4 ReefcarnBG; F3 Schoolfish1; F2 Scombr/Jacks; F5 Schoolfish2; I6 Zoopankton; Benthic prod.; I1 Cephalopods; Phytoplankton; R1 Sea turtles; F7 Biggroupers; B1 Sea birds\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Looe Key National Marine Sanctuary (1980)}, $\rho = 0.263026$} \\
\hline
Decomp/Microf; LgReefHerbivore; SmReefHerbivore; Sessile Animals; Crustaceans; Worms/Molluscs; Echinoderms; SmReefCarnivore; Sharks/Rays; LgReefCarnivore; Large Planktiv.; Sm.Planktivores; Zooplankton; Cephalopods; Benthic prod.; Midwater Pisc.; Phytoplankton; Sea Turtles; Lg.Groupers\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Thermaikos Gulf (1998)}, $\rho = 0.262715$} \\
\hline
Zooplankton; Benthic small crustaceans; Benthic invertebrates; Polychaetes; Shrimps; Crabs; Seabirds; Red mullets; Loggerhead turtle; Other small pelagics; Octopuses and cuttlefish; Horse mackerels; Mackerels; Other gadiforms; Flatfishes; Squids; Hake; Rays and skates; Demersal fishes 2; Sardine; Sharks; Demersal fishes 3; Picarels and bogue; Anchovy; Demersal fishes 4; Demersal fishes 1; Anglerfish; Medium pelagics; Phytoplankton; Large pelagics; Dolphins\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Guinea (1985)}, $\rho = 0.260576$} \\
\hline
Large zooplankton; Small zooplankton; Benthos; Crustacea; Cephalopods; Mullets+; Sardinella+; Horse mackerels+; ML demersal invert.eaters; S. demersal invert.eaters; Seabream+; SM demersal pred.eaters; L. demersal pred.eaters; Bobo croaker; Sea birds; Barracudas+; Carangids; Other croakers; Sharks+; Large pelagics; Primary producers; Rays+; Sea catfish; Dolphins; Ethmalosa; Bathy-dem pred.eaters; Grunts+; Giant Afr. threadfin; Bathy-dem invert.eaters; Turtles; Soles+; Lesser Afr. threadfin; Royal threadfin; Whales\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bay of Biscay (1970)}, $\rho = 0.260490$} \\
\hline
Small Deepwater; Worms; Zooplankton Large; Molluscs; Sponges/Epibenthic; Shrimps/Prawns; Echinoderms; Crabs; Benthic Infauna; Cephalopods; Medium (Big end) Demersal  High Troph; Small Demersal; Medium Pelagic; Really Small Demersal High Troph; Extra Large Demersal Low Troph; Medium (Small end) Demersal; Large Pelagic; Large Demersal; Rays/Skates; Small Sharks; Extra Large Demersal High Troph; Large Deepwater; Large Sharks; Zooplankton Small; Small Pelagic Low Troph; Anchovy; Really Small Demersal Low Troph; Sardine; Small Pelagic High Troph; Toothed Cetaceans; Primary Producers; Medium Deepwater; Baleen Whales; Birds; Extra Large Pelagic; Tuna-like fish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bolinao Coral Reef (1980)}, $\rho = 0.259586$} \\
\hline
Molluscs; Sea cucumber; Sea Urchins; Siganus fusc.; Zooplankton; Ot.invertebr.; Siganus spinus; Damselfishes; Coral.cons.; Crustaceans; Ot.herbiv.f.; Ot.omniv.f.; Ot.planktiv.f.; Ot.pisciv.f.; Gobies; Moray; Cardinalfishes; Parrotfish; Squid; Coral.prod.; Phytoplankton; Seagrass; Seaweeds; Wrasse (c.a.); Groupers (e.m.)\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Mauritanie (1991)}, $\rho = 0.259077$} \\
\hline
mesozooplankton; BA mesozooplankton; BA meiobenthos; shelf meiobenthos; shelf molluscs; shelf worms; BA worms; BA molluscs; Mullets; BA crustaceans; shelf crustaceans; shelf other inverts; BA other inverts; Cephalopods; macrozooplankton; BA macrozooplankton; BA L crustaceans; shelf L crustaceans; Horse mackerels; Coastal M; Shelf M; Mackerel; Croakers ad; Sardinelles; Sparids ad; Coastal birds; Catfish ad; Groupers ad; Shelf L; Seabreams ad; Coastal selacians; Shelf S ; Coastal S; Sparids juv; Seabreams juv.; Sardine; Shelf soles; Shelf selacians; Croakers juv; Catfish juv; Pelagic L; algae and eelgrass; BA phytoplankton; phytoplankton; Octopus vulgaris; Scianids; Grouper juv; Meagre juv; Meagre ad; Marine mammals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sinaloa sur Mexico (1994)}, $\rho = 0.258644$} \\
\hline
Gastropoda; Macrocrustáceos; Polychaeta; Zooplancton; Penaeidae; Celenterata; Porifera; Bivalvia; Stomatopoda; Otros peces; Portunidae; Pleuronectiform; Carangidae; Echinodermata; Serranidae; Lutjanidae; Coryphaenidae; Mugilidae; Gerreidae; Clupeidae; Ariidae; Rajiformes; Macrofitas; Sciaenidae; Cephalopoda; Cheloniidae; Haemulidae; Poly./Mullidae; Scorp./Triglida; Scombridae; Fitoplancton; Palinura; Tetraodontidae; Centropomidae; Aves; Synodontidae\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{South western Gulf of Mexico (1970)}, $\rho = 0.255661$} \\
\hline
Annelids; Zooplankton; Microcrustacean; Molluscs; Crabs; Shrimps; Other fishes; Herrings; Jacks; Flounder; Catfish; Red grouper; Sharks; Benthic prod.; Anchovies; Red snapper; Mojarra; Phytoplankton; Seatrout; Grunts; Lizard fish; Span. mackerel; King mackerel\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Hudson Bay (1970)}, $\rho = 0.255132$} \\
\hline
MicroZooplankton; Copepods; Other Benthos; Bivalves; Marine Worms; Other MesoZooplankton; Crustaceans; Euphausids; MacroZooplankton; Other Marine Fish; Sandlance; Capelin; Brackish Fish; Seabirds; Echinoderms; Cephalopods; Atlantic Salmon; Arctic Char; Gadiformes; Sculpins/ Zoarcids; Killer Whale; SH Polar Bear; Polar Bear WHB; Polar Bear Foxe; Sharks/Rays; Walrus S; Ice Algae; Primary Production; Walrus N; Bowhead; Beluga E; Bearded Seal; Beluga James; Beluga W; Harbour Seal; Narwhal; Ringed Seal; Harp seal\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{West Florida Shelf Historic Model (1950)}, $\rho = 0.254249$} \\
\hline
Microbial Heterotrophs; Mullets; Bivalves; Small Copepods; Sessile epibenthos; Meiofauna; Small infauna; Other Mesozooplankton; Small mobile epifauna; Echinoderms Large gastropods; Ichthyoplankton; CarnivZooplank; Anchovies and silversides; Adult Shrimps; coastal omnivores; Sardine Herring Scad complex; Stomatopods; Squid; Large Crabs; small coastal carnivores; reef carnivores; large coastal carnivores; oceanic small pelagics; black grouper 0; jacks wahoo dolphinfish tunnies; black grouper 1; other snapper; Rays skates; Red snapper juv; reef omnivores; Billfish Tuna; CarnivJellyfish; tilefish; Large coastal sharks; Black sea bass; king mackerel adult; Small coastal sharks; Octopods; Lobsters; other shallow water grouper; red grouper 1; amberjacks/rudderfish; coastal piscivores; red grouper 0; Vermilion snapper; gag 0; Spanish mackerel juv; gag 1; yellowedge grouper 0; king Mackerel juv; red snapper adult; Spanish mackerel adult; Phytoplankton; triggerfish; Yellowedge grouper 1; Cobia; red grouper 3; other deep water grouper; black grouper 3; goliath grouper; yellowedge grouper 3; gag 3; Dolphins; Seabirds; Macroalgae; Sea grasses; Microphytobenthos\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{West Scotland (2000)}, $\rho = 0.253368$} \\
\hline
Epifauna; Infauna; Small zooplankton; Polychaetes; Large zooplankton; Euphausiids; Prawns/shrimps; Halibut/turbot/brill; Other benthic inverts; Echinoderms; Other demersals; Gurnards; Other pelagics; Cod; Saithe; Herring; Sharks; Seals; Cetaceans; Haddock; Seabirds; Cephalopods; Rays/Skates; Whiting; Mackerel; Crabs/lobsters; Salmo; Trachurus; Phytoplankton; Sprat; Sandeel; Norway pout; Nephrops; Sole; Plaice; Inshore fish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Celtic Sea (1985)}, $\rho = 0.252559$} \\
\hline
Bacteria; Commercial bivalves; Suspension/Surface detritus feeder benth. inv.; Mesozooplankton - Small; Benthic meiofauna; Microzooplankton; Mesozooplankton - Large; Macrozooplankton; Suprabenthos; Subsurface deposit feeder benth. inv.; Carnivorous/Necrophagous benth. inv.; Shrimps; Horse mackerel; Benthic cephalopods; Commercial crustaceans; Mackerel; Nephrops; Squids; Epibenthivorous demer. fish; Pouts; Pelagic sharks; Benthivorous demer. elasmobranchs; Hake large; Pilchard; Cod small; Hake small; Cod large; Anglerfish large; Anglerfish small; Pelagic fish - Medium; Small benthivorous demer. fish; Sea bass; Toothed cetaceans / Seals; Megrim; Carnivorous demer. elasmobranchs; Piscivorous demer. fish; Whiting; Pelagic fish - Large; Herring; Suprabenthivorous demer. fish; Sprat; Endobenthivorous demer. fish; Blue whiting; Seabirds - Surface feeders; Seabirds - Divers; Phytoplankton - Large; Phytoplankton - Small; Boarfish; Sole; Plaice; Haddock; Baleen whales\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Galapagos, Floreana rocky reef (2000)}, $\rho = 0.250728$} \\
\hline
Herbivorous zooplankton; Small benthic invertebrate eaters; Filter + suspension feeders; Lytechinus urchin; Other sea cucumbers; Small crustaceans; Shrimps and small crabs; Tripneustes urchin; Parrotfishes; Other urchins; Pepino sea cucumber; Small gastropods; Detritivorous fish; Chitons; Stony corals; Worms and ophioroids; Anemones; Eucidaris urchin; Other herbivorous fish; Asteroids; Omnivorous reef fishes; Large benthic invertebrate eaters; Non-commercial reef predators; Octopods; Slipper lobster; Spiny lobsters; Hexaplex gastropod; Sharks; Carnivorous zooplankton; Planktivorous reef fish; Pelagic planktivores; Sea lions; Birds; Toothed cetaceans; Benthic algae; Microphytobenthos; Phytoplankton; Marine iguana; Sea turtles; Other commercial reef predators; Pelagic predators; Bacalao\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{USA, South Atlantic Continental Shelf (1995)}, $\rho = 0.250650$} \\
\hline
Zooplankton; Bivalves; Benthic macrofauna (and meiofauna); Sessile epibenthos; Echinoderms and gastropods; Demersal omnivores; Shrimp; Crabs; Other fishes; Jellies; Forage fishes; Stomatopods; Demersal invertebrate-eaters; Lobsters; Benthic piscivores; Benthic rays/skates; Flounder; Drum and croaker; Marine birds; Demersal piscivores; Snappers; Mackerel; Groupers; Pelagic planktivores; Toothed cetaceans; Sharks  (and alligators); Tuna; Macroalgae; Squid; Jacks; Benthic invertebrate-eaters; Pelagic piscivores; Microphytobenthos; Sea grasses; Billfishes; Phytoplankton; Manatees; Sea turtles; Demersal planktivores; Baleen whales; Octopods\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Mondego Estuary - Zostrea site}, $\rho = 0.249118$} \\
\hline
Hydrobia ulvae; Melita palmata; Ampithoe ferox; Gibulla; Littorina; Cyathura carinata; Scrobicularia plana; Cerastoderma edule; Modiolus; Amage adspersa; Capitella capitata; Heteromastus filifor; Oligochaeta; Other detrivors; Sphaeroma hookeri; Idotea chelipes; Lumbrineris impatien; Microalgae and detri; Diopatra neapolitana; Nereis diversicolor; Carcinus maenas; Crangon crangon; Macrofauna predators; Nephtys; Other predatory inve; Endofauna consumers; Larus fuscus; Zooplankton; Trigla lucerna; Larus ridibundus; Phytoplankton; Enteromorpha sp; Ulva lactuca; Zostera; Epiphytes; Gracilaria; Kentish Plover; Zooplankton consumer; Pomatoschistus minut; Grey Plover; Dunlin; Ringed Plover\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern Gulf of St Lawrence (1990)}, $\rho = 0.245275$} \\
\hline
Echinoderms; Molluscs; Other bent. invert.; Small zooplankton; Large zooplankton; Shrimp; Polychaetes; Large crustacea; Flounders; Sand lance; S. demersals; Skates; American plaice; Capelin; Redfish; Small cod; S. Greenland halibut; Arctic cod; Planktivorous small pelagics; Piscivorous small pelagics; Large pelagics; Large cod; L. demersals; L. Greenland halibut; Phytoplankton; Cetacea; Seabirds; Harp seals; Harbour seals; Grey seals; Hooded seals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sonda Campeche Act (1988)}, $\rho = 0.244000$} \\
\hline
Infauna; Zooplancton; Epifauna; Camarón; Pulpo; Mojarras; Bagres; Lenguados; Roncos; Meros; Sierras; Tiburones; Otros peces; Pargos; Sardinas; Corvinas; Jureles; Macrofítas bent.; Sargos; Fitoplancton; Tortugas marinas; Calamar; Aves marinas; Delfines\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Crystal River Creek - Control}, $\rho = 0.243537$} \\
\hline
benthic invertebrates; mullet; zooplankton; sheepshead killifish; goldspotted killifish; striped anchovy; bay anchovy; silver jenny; moharra; silverside; pinfish; longnosed killifish; microphytes; gulf killifish; macrophytes; sheepshead; blacktip shark; needlefish; stingray; gulf flounder\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Raja Ampat (2005)}, $\rho = 0.242949$} \\
\hline
Infaunal invertebrates; Jellyfish and hydroids; Shrimps and prawns; Penaeid shrimps; Hermatypic scleractinian corals; Non reef building scleractinian corals; Azooxanthellate corals; Soft corals; Sea cucumbers; Epifaunal detritivorous invertebrates; Epifaunal carnivorous invertebrates; Bivalves; Sessile filter feeders; Adult scraping grazers; Juvenile macro algal browsing; Detritivore fish; Juvenile scraping grazers; Juvenile medium reef associated; Adult macro algal browsing; Small crabs; Large crabs; Juvenile small planktivore; Juvenile small reef asociated; Juvenile small pelagic; Adult small reef associated; Juvenile butterflyfish; Juvenile small demersal; Juvenile large reef associated; Adult large reef associated; Adult medium reef associated; Octopus; Adult small demersal; Adult butterflyfish; Adult large demersal; Anemonies; Adult small planktivore; Juvenile deepwater fish; Adult small pelagic; Cleaner wrasse; Adult large planktivore; Squid; Juvenile medium pelagic; Adult medium pelagic; Juvenile Napoleon wrasse; Adult large sharks; Juvenile small sharks; Adult rays; Juvenile large planktivore; Juvenile large demersal; Subadult Napoleon wrasse; Skipjack tuna; Adult snappers; Juvenile large pelagic; Adult large pelagic; Adult deepwater fish; Subadult snappers; Birds; Adult Napoleon wrasse; Juvenile large sharks; Mackerel; Other tuna; Lobsters; Adult eroding grazers; Giant triton; Carnivorous zooplankton; Large herbivorous zooplankton; Small herbivorous zooplankton; Phytoplankton; Adult anchovy; Herbivorous echinoids; Juvenile anchovy; Subadult groupers; Adult groupers; Green turtles; Juvenile eroding grazers; Crown of thorns; Billfish; Crocodiles; Juvenile groupers; Juvenile snappers; Sea grass; Reef associated turtles; Juvenile rays; Oceanic turtles; Manta ray; Whale shark; Juvenile coral trout; Adult coral trout; Adult small sharks; Macro algae; Calcareous algae; Mangroves; Dugongs; Mysticetae; Deepdiving odontocetae; Piscivorous odontocetae\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Independence Bay (1996)}, $\rho = 0.242895$} \\
\hline
zooplankton; littoral fish ; benthic detrivores; herbivorous gastropods; scallops; polychaetes; sea urchins; misc. filter feeders; predatory gastropods; small carnivores; sea stars; predatory crabs; small pelagic fish; pelagic predatory fish ; octopus ; macroalgae; Phytoplankton; sea birds; marine mammals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Raja Ampat (1990)}, $\rho = 0.242618$} \\
\hline
Infaunal invertebrates; Jellyfish and hydroids; Shrimps and prawns; Penaeid shrimps; Hermatypic scleractinian corals; Non reef building scleractinian corals; Azooxanthellate corals; Soft corals; Sea cucumbers; Epifaunal detritivorous invertebrates; Epifaunal carnivorous invertebrates; Bivalves; Sessile filter feeders; Adult scraping grazers; Juvenile macro algal browsing; Detritivore fish; Juvenile scraping grazers; Juvenile medium reef associated; Adult macro algal browsing; Small crabs; Large crabs; Juvenile small planktivore; Juvenile small reef asociated; Juvenile small pelagic; Adult small reef associated; Juvenile butterflyfish; Juvenile small demersal; Adult large reef associated; Adult medium reef associated; Adult butterflyfish; Adult large demersal; Juvenile large reef associated; Octopus; Adult small demersal; Anemonies; Juvenile deepwater fish; Adult small planktivore; Cleaner wrasse; Adult small pelagic; Adult large planktivore; Juvenile Napoleon wrasse; Birds; Adult large sharks; Squid; Juvenile medium pelagic; Adult medium pelagic; Juvenile small sharks; Adult rays; Juvenile large planktivore; Juvenile large pelagic; Juvenile large demersal; Adult large pelagic; Skipjack tuna; Adult deepwater fish; Juvenile large sharks; Mackerel; Adult snappers; Subadult snappers; Herbivorous echinoids; Other tuna; Adult eroding grazers; Giant triton; Carnivorous zooplankton; Large herbivorous zooplankton; Subadult Napoleon wrasse; Adult Napoleon wrasse; Small herbivorous zooplankton; Phytoplankton; Subadult groupers; Adult groupers; Adult anchovy; Juvenile anchovy; Green turtles; Juvenile eroding grazers; Lobsters; Crown of thorns; Crocodiles; Billfish; Juvenile groupers; Juvenile snappers; Sea grass; Reef associated turtles; Juvenile rays; Oceanic turtles; Manta ray; Whale shark; Juvenile coral trout; Adult coral trout; Adult small sharks; Macro algae; Calcareous algae; Mangroves; Dugongs; Mysticetae; Deepdiving odontocetae; Piscivorous odontocetae\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Tagus estuary, Portugal }, $\rho = 0.242040$} \\
\hline
Crassostrea angulata; Scrobicularia plana, Cerastodenlla; Mytilus; bacteria; Gammaridae; Coropllium; Cirratulidae, Capitellidae, Maldanidae; meiofauna; Carcillus maellas; Crangon; Nereis diversicolor; Nereis succinea; Chelon labrosus, Liza ramada, L. aurata; Ulva, Iteromoplla; Conter conger; phytoplankton; birds; Mysidacea; Copepoda; Ciliata mustela; Dicentrarcllus labrax; Pomatoscllistus minutus; Ellgraulis encrasicolus; Sardina pilcllardus; Clupeidae; Solea vulgaris; Trigla lucerna\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Morocco (1985)}, $\rho = 0.241521$} \\
\hline
Lg. zooplankton; Other benthos; Worms; Sm. deep water bottom; Detrital feeders; Shrimp; Crabs; Predatory echinoderms; Sm. demersal; Cephalopods; Med. demersal comm.; Sardines; Med. demersal; Tunas; Lg. demersal comm.; V. lg. demersal comm.; Lg. demersal sharks/rays; Sm. zooplankton; Sm. bathypelagic; Med. pelagic comm.; Pelagic sharks; Mesopelagic prey; Lg. bathypelagic; Toothed whales/dolphins; Lg. demersal; Med. pelagic; Sm. demersal sharks/rays; Lg. pelagic; Primary producers; Turtles; Lobsters; Lg. deep water bottom; Med. bathypelagic; V. lg. demersal; Seabirds; Lg. deep water comm.; Baleen whales\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Calvi Bay (1998)}, $\rho = 0.240741$} \\
\hline
Protozoa; Ot. Crustacea; Pel. Bacteria; Herb. Fish; Echinoderms; Amphipods; Gastropods; Polychaetes; Susp. Feeders; Decapods; Inv. Feeders 4; Zooplankton; Sea Birds; Macroalgae; Piscivores; M-carnivores; Inv. Feeders 1; Macro-Plankton; Phytoplankton; Inv. Feeders 3; Plankt. Fish; Mugil spp.; Blennies; D. puntazzo; Inv. Feeders 2; Cephalopods\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Mangrove Estuary - Dry Season}, $\rho = 0.240059$} \\
\hline
INSCT; MICR. H2O; EPIFN; BACT.SED.; VULT; TCRAB; BVLVS; AMPHI; SCRUST; PENAID; DCRAB; CARID; MANA; LARV; POEC; BEAR; FWINV; OSHMP; MERO; ZOOPL.; AGAST; OPSU; TGAST; OCRAB; PCRAB; DUCK1; FLA. SED.; CIL. SED.; KILLI; MULL; POLY; MEIOF.; MBENTH; DUCK2; GOBY; TURT; JLOBST; PIN; RACO; HERR; ANCH; FWFSH; BENTH; MOJA; RAYS; SNKS; SLVR; COCO; OFISH; MRAPT; FOX; CATS; HRSE; OTH. PP; K \& H; OWLS; SPIDR; SCIAE; EFISH; SNAP; NEED; AMPH; SNOOK; LZRD; TARP; LEAF; CUDA; PASSOMN; WOODP; C \& C; PASSPERD; SSBIRDS; G \& T; GUIF; SE \& E; IBIS; BH \& E; SHRK; L \& G; DUCK3; CORM; PELC; DOLP; PHY; WOOD; ROOT; RABT; SQIUR; DERS; M \& R; M \& O\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Mangrove Estuary - Wet Season}, $\rho = 0.239816$} \\
\hline
INSCT; MICR. H2O; EPIFN; BACT.SED.; VULT; TCRAB; BVLVS; AMPHI; SCRUST; PENAID; CARID; DCRAB; MANA; LARV; POEC; FWINV; BEAR; OSHMP; OCRAB; PCRAB; MERO; ZOOPL.; AGAST; DUCK1; TGAST; OPSU; FLA. SED.; KILLI; CIL. SED.; POLY; MEIOF.; MBENTH; MULL; DUCK2; GOBY; TURT; RACO; JLOBST; HERR; ANCH; PIN; FWFSH; BENTH; MOJA; RAYS; SNKS; COCO; SLVR; OFISH; MRAPT; HRSE; OTH. PP; CATS; FOX; K \& H; OWLS; SPIDR; SCIAE; EFISH; SNAP; NEED; AMPH; SNOOK; LZRD; TARP; LEAF; CUDA; PASSOMN; WOODP; C \& C; PASSPERD; SSBIRDS; G \& T; GUIF; SE \& E; IBIS; BH \& E; SHRK; L \& G; DUCK3; PELC; CORM; DOLP; PHY; WOOD; ROOT; RABT; SQIUR; DERS; M \& R; M \& O\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Mauritania (1987)}, $\rho = 0.238115$} \\
\hline
micro zooplancton; meso zooplancton; mugilides; macrobenthos; crustaces non-comm; crustaces comm; dem S inv; dem L pred; cephalopodes comm; macrozooplancton; clupeides; maquereau; chinchards; cephalopodes non-comm; mesopel pred; dem M inv; bathydem S pred; Selaciens L pred; sabres; dauphins; merlu; Selaciens L inv; pel L pred; mesopel inv; pel M planc; dem S pred; dem M pred; sparides comm; thon hauturier; producteurs primaires; bathydem S inv; dem L inv; pel L inv; thon cotier; raie M; oiseaux; orque\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Mauritania (1998)}, $\rho = 0.237872$} \\
\hline
micro zooplancton; meso zooplancton; mugilides; macrobenthos; crustaces non-comm; crustaces comm; dem S inv; dem L pred; cephalopodes comm; macrozooplancton; clupeides; maquereau; chinchards; cephalopodes non-comm; mesopel pred; dem M inv; bathydem S pred; sabres; Selaciens L pred; dauphins; merlu; Selaciens L inv; pel L pred; mesopel inv; pel M planc; dem S pred; dem M pred; sparides comm; thon hauturier; producteurs primaires; bathydem S inv; dem L inv; pel L inv; thon cotier; raie M; oiseaux; orque\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bay of Biscay (1998)}, $\rho = 0.237602$} \\
\hline
Zooplankton Large; Small Deepwater; Crabs; Worms; Molluscs; Sponges/Epibenthic; Shrimps/Prawns; Echinoderms; Cephalopods; Medium Pelagic; Medium (Big end) Demersal  High Troph; Extra Large Demersal Low Troph; Medium (Small end) Demersal; Large Pelagic; Large Demersal; Rays/Skates; Small Sharks; Extra Large Demersal High Troph; Large Deepwater; Really Small Demersal High Troph; Large Sharks; Zooplankton Small; Small Pelagic Low Troph; Small Demersal; Small Pelagic High Troph; Really Small Demersal Low Troph; Anchovy; Sardine; Benthic Infauna; Toothed Cetaceans; Primary Producers; Baleen Whales; Medium Deepwater; Birds; Extra Large Pelagic; Tuna-like fish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Cape Verde (1981)}, $\rho = 0.237253$} \\
\hline
Zooplankton; Microfauna; Herbivores; Heterotrophic b; Molluscs/Worms; Echinoderms; Crustaceans; Small pelagics; O Demersal fish; Demersal sharks; Flatfish; Rays; Pelagic sharks; Benthic autotro; Sparids; Reef feeders; Large Tuna; Demersal predat; Pelagic predato; Small tuna; Demersal fish; Flyingfish; Jacks; Bathydemersal; Phytoplankton; Turtles; Sea birds; Moray eels; Billfish; Mammals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Galapagos (2006)}, $\rho = 0.235595$} \\
\hline
Predatory zooplankton; Herbivorous zooplankton; Mullets; Herbivorous benthic fishes; Sea cucumbers; Small herbivorous gastropods; Sponges and polychaetes; Stony corals; Sea stars and sea urchins; Benthic omnivorous fishes; Small benthic predatory fishes; Benthic predatory fishes; Shrimps and small crabs; Anemones and zoanthids; Small predators gastropods; Parrotfishes; Lobsters; Sharks; Predatory macroinvertebates; Rays; Planktivorous reef fishes; Small planktivorous reef fishes; Macroalgae; Predatory marine mammals; Phytoplankton; Zooxanthella; Sea turtles; Groupers; Pelagic predatory fish; Dolphins; Hammerhead sharks; Seabirds\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Irish Sea (1973)}, $\rho = 0.233265$} \\
\hline
Infauna (Polycheate); Herbivorous Zooplankton; Meiofauna; Infaunal Mesobenthos; Prawns and Shrimp; Sessile Epifauna; Lobster and Large Crabs; Omnivorous Zooplankton; Carnivorous Zooplankton; Epifaunal Macrobenthos; Gelatinous Zooplankton; Cephalopods; Infaunal Macrobenthos; Sandeels; Nephrops; Mackerel; Other Small Gadoids; Whiting; Skates and Rays; Epifaunal Mesobenthos; Adult Cod 2+; Seabirds; Baleen Whales; Toothed Whales; Medium Flatfish; Small Pelagic Planktivorous Fish; Adult Haddock 2+; Other Small Demersal; Dragonets; Phytoplankton; Other Large Gadoids; Monkfish; Juvenile Haddock Age 1; Juvenile Cod Age 1; Gurnards; Juvenile Plaice Age 1; Small Flatfish; Sole; Adult Plaice 2+; Other Large Demersals; Mullet; Seatrout; Small Sharks; Large Flatfish; Large Sharks; Bass; Microflora; Seaweed; Basking Sharks; Seals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Antarctic (1970)}, $\rho = 0.232855$} \\
\hline
Copepods; Hemichordata; Holothuroidea; Micro-Zooplankton; Macro-Zooplankton; Porifera; Bryozoa; Mollusca; Urochordata; Krill Sub-adult; Brachiopoda; Asteroidea; Arthropod Crustecea; Crinoidea; Worms; Krill Adult; Arthropod Other; Cnidaria; Small Nototheniidae; Salps; Pleuragramma antarcticum; Other Pelagics; Cephalopods; Other Icefish; Large Nototheniidae; Toothfish; Ophiuroidea; Echinoidea; Killer Whales; Leopard Seal; Notothenia gibberifrons; Deep demersals Small; Deep demersals Large; Myctophids; Champsocephalus gunnari; Cryptophytes; Other Phytoplankton; Diatoms; Ice algae; Shallow Demersals; Flying birds; Krill Juvenile; Krill Larvae; Minke whales; Fin Whales; Humpback whales; Blue Whales; Crabeater Seal; Adelie Penguins; Macaroni Penguin; Antarctic Fur Seals; Emperor penguins; Chinstrap Penguins; Gentoo Penguins; Weddell Seal; Ross Seal; Sperm whales; Southern Elephant Seals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Peru (1973)}, $\rho = 0.232368$} \\
\hline
Zooplankton; Meiobenthos; Makrobenthos; Anchoveta; Sardine; Other pelagics; Hake; Other demersals; Horse mackerel; Mackerel; Benthic prod.; Phytoplankton; Cormorant; Booby; Pelican; Bonito; Fur seal; Other mammals; Sea lion\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Albatross Bay (1986)}, $\rho = 0.229843$} \\
\hline
Benthic herbivores; Estuarine microbial heterotrophs; Estuarine zooplankton; Estuary detritivores; Insects; Marine microbial heterotrophs; Marine zooplankton; All other non-commercial prawns; Small benthopelagic invert feeders; Small benthic invert feeders; Small pelagic piscivores; Turtles; Small benthic piscivores; Echinoids; Estuary  pelagic herbivores; Estuarine bivalves; Banana prawn adult; Marine bivalves; Ophioroids; Holothurians; Marine worms; Estuarine worms; Marine small crustaceans; Marine small gastropods; Other large crabs; Marine meiofauna; Estuarine meiofauna; Sessile epibenthos; estuarine small crustaceans; Estuarine small gastropods; Spatangoids; Estuary small benthic invert feeders; Squid and cuttlefishes; Estuarine ichthyoplankton; Small jellies; Asteriods; Marine ichthyoplankton; Large jellies; Crayfish; The mud crab; Red mud crab; Sand crab; Thallasinid prawns (Callianassa); All other commercial prawns; Estuary large benthic pisc/prawn feeders; Stomatopods; Octopus; Dolphins; Estuary planktivores; Small pelagic planktivores; Estuary lg teleost benthopelagic posc/prawn feeder; Medium pelagic piscivores; Estuary lg elasmo benthopelagic pisc/prawn feeders; Estuary benthic herbivores; Crocodiles; Marine forams; Mangroves; Seagrass; Estuary insectivores; Large elasmo benthopelagic piscivores; Large benthopelagic invert feeders; Large teleost benthopelagic piscivores; Estuarine macroalgae; Banana prawn juvenile; Tiger prawn subadults; Tiger prawn juvenile; Dugongs; Tiger prawn adult; Polychaete feeders; Estuarine phytoplankton; Large gastropods; Estuary polychaete feeders; Banana prawn subadults; Estuary large benthic invert feeders (Rays); Estuary large benthopelagic invert feeders; Scavengers; Large teleost benthic piscivores; Microphytobenthos; Marine phytoplankton; Marine macroalgae; Large pelagic planktivores; Large elasmo benthic invert feeders; Small benthopelagic piscivores; Large teleost benth invert feeders; Common terns; Large pelagic piscivores; Brown boobies; Sawfishes; Crested terns; Lesser frigates; Sea snakes; Estuarine forams\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Peru (1960)}, $\rho = 0.228684$} \\
\hline
Meiobenthos; Makrobenthos; Zooplankton; Anchoveta; Sardine; Other pelagics; Other demersals; Horse Mackerel; Mackerel; Hake; Benthic prod.; Phytoplankton; Bonito; Sea lion; Other mammals; Fur seal; Booby; Cormorant; Pelican\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sechura Bay (1996)}, $\rho = 0.228458$} \\
\hline
Zooplankton; littoral fish; Benthic detrivores; Herbivorous gastropods; Scallops; Polychates; Sea urchins; Misc. filter feeders; Small carnivores; Pedratory gastropods; Predatory crabs; sea stars; small pelagic fish; pelagic predatory fish; octopus; Macroalgae; Phytoplankton; cephalopods; sea birds ; marine mammals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Western Tropical Pacific Ocean (1990)}, $\rho = 0.228158$} \\
\hline
mesozooplankton; crustacea; epipelagic fish; mesopelagic fish; piscivorous fish; small sharks; other sharks; small scombrids; Other billfish; cephalopods; small billfish; skipjack tuna; yellowfin tuna; small phytoplankton; bigeye tuna; large phytoplankton; microzooplankton; Blue shark; Swordfish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Middle Chesapeake Bay}, $\rho = 0.227775$} \\
\hline
Free Bacteria; Particle Attached Bacteria; Benthic Bacteria; Suspension Feeding Benthos; Deposit Feeding Benthos; Menhaden; Meiofauna; Meroplankton; Mesozooplankton; Bay anchovy; Spot; Blue Crab; Croaker; Hogchoker; Catfish; White Perch; Rotifers; Ciliates; Ctenophores; Net Phytoplankton; Picoplankton; Heteroflagellates; American eel; Striped Bass; Weakfish; Bluefish; Chrysaora; Microphytobenthos; SAV\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Peru (1953)}, $\rho = 0.227763$} \\
\hline
Meiobenthos; Makrobenthos; Zooplankton; Anchoveta; Sardine; Other pelagics; Other demersals; Horse Mackerel; Mackerel; Hake; Benthic prod.; Phytoplankton; Cormorant; Booby; Pelican; Sea lion; Fur seal; Other mammals; Bonito\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sierra Leone (1990)}, $\rho = 0.226960$} \\
\hline
Carnivorous zooplankton; Herbivorous zooplankton; Benthos; Mullets and other herbivores; Sardinellas; Scads and mackerels; Crustaceans; Cephalopods; Small pelagic invert feeders; Small demersal predators; Small demersal invert feeders; Medium demersal invert feeders; Sickle-and spadefish; L Coastal Sharks and Rays; Large pelagic predators; Croackers; Large demersal predators; Large demersal invert feeders; Jacks; Small Tuna; L Deep Sharks and Rays; Bongo shad; Large Tuna; M Coastal Sharks and Rays; Mesopelagics; M Deep Sharks and Rays; Catfish; Toothed whales and dolphins; Baleen whales; Royal Threadfin; Lesser African Threadfin; Large Bathypelagic predators; Large Bathydem predators; Primary producers; Small pelagic predators; Turtles; M Bathypelagic invert feeders; SM Bathydem invert feeders; Seabirds; Medium demersal predators; Small Bathypelagic predators; Gaint African Threadfin; Groupers\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Narragansett Bay Model}, $\rho = 0.226941$} \\
\hline
Mesozooplankton; Microzooplankto; Shrimp(Pal,Crg); Menhaden; Bay Anchovy; Pelag Bacteria; SusPoc Bacteria; SedPOC Bacteria; Hard Clam; Ben Meiofauna; Ben Macrofauna; Cancer Crabs; Mummichog; Hetero Microflag; Striped Bass; Dogfish; Phytoplankton; Butterfish; Am. Lobster; Longfin Squid; Bluefish; Fish Larvae; Benthic Alage; Softshell Clam; Atl Silversides; Windowpane; Ctenophores; Scup; Skates; Winter Flounder; Tautog\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sierra Leone (1978)}, $\rho = 0.226864$} \\
\hline
Carnivorous zooplankton; Herbivorous zooplankton; Benthos; Mullets and other herbivores; Sardinellas; Scads and mackerels; Crustaceans; Cephalopods; Small pelagic invert feeders; Small demersal predators; Small demersal invert feeders; Medium demersal invert feeders; Sickle-and spadefish; L Coastal Sharks and Rays; Large pelagic predators; Croackers; Large demersal predators; Large demersal invert feeders; Jacks; Small Tuna; L Deep Sharks and Rays; Bongo shad; Large Tuna; Mesopelagics; M Coastal Sharks and Rays; M Deep Sharks and Rays; Catfish; Toothed whales and dolphins; Baleen whales; Royal Threadfin; Lesser African Threadfin; Large Bathypelagic predators; Large Bathydem predators; Primary producers; Small pelagic predators; Turtles; M Bathypelagic invert feeders; SM Bathydem invert feeders; Seabirds; Medium demersal predators; Gaint African Threadfin; Small Bathypelagic predators; Groupers\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{West Baffin Bay, Coastal and Shelf (2016)}, $\rho = 0.225939$} \\
\hline
Bacteria; Microzooplankton; Calanus; Omnivorous zooplankton; Other benthos; Bivalves; Polychaetes; Echinoderms; Large crustaceans; Greenland shark; Sculpins/Eelpouts; Carnivorous zooplankton; Greenland halibut; Cephalopods; Killer whale; Polar bear; Arctic/Polar cod; Small demersal fish; Small pelagic fish; Arctic char; Large demersal fish; Ice algae; Phytoplankton; Walrus; Bowhead whale; Seabirds; Ringed seal; Other seals; Narwhal\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Benguela (1967)}, $\rho = 0.224793$} \\
\hline
Microzooplankto; Meiobenthos; Pelagic Goby; Macrobenthos; Gelatinous zoop; Other small pel; Large M. capens; Large M. parado; cephalopods; Chondrichthyans; Benthic-feeding; Phytoplankton; Mesozooplankton; Macrozooplankto; Pelagic-feeding; Cetaceans; Seabirds; Seals; Large pelagics; Mesopelagics; Sardine; Anchovy; Juvenile horse; Adult horse mac; Small M. capens\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Benguela (1900)}, $\rho = 0.224793$} \\
\hline
Microzooplankto; Meiobenthos; Pelagic Goby; Macrobenthos; Gelatinous zoop; Other small pel; Large M. capens; Large M. parado; cephalopods; Chondrichthyans; Benthic-feeding; Phytoplankton; Mesozooplankton; Macrozooplankto; Pelagic-feeding; Cetaceans; Seabirds; Seals; Large pelagics; Mesopelagics; Sardine; Anchovy; Juvenile horse; Adult horse mac; Small M. capens\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Benguela (1600)}, $\rho = 0.224793$} \\
\hline
Microzooplankto; Meiobenthos; Pelagic Goby; Macrobenthos; Gelatinous zoop; Other small pel; Large M. capens; Large M. parado; cephalopods; Chondrichtians; Benthic-feeding; Phytoplankton; Mesozooplankton; Macrozooplankto; Pelagic-feeding; Cetaceans; Seabirds; Seals; Large pelagics; Mesopelagics; Sardine; Anchovy; Small Horse mac; Large horse mac; Small M. capens\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Benguela (1990)}, $\rho = 0.224793$} \\
\hline
Microzooplankto; Meiobenthos; Pelagic Goby; Macrobenthos; Gelatinous zoop; Other small pel; Large M. capens; Large M. parado; cephalopods; Chondrichthyans; Benthic-feeding; Phytoplankton; Mesozooplankton; Macrozooplankto; Pelagic-feeding; Cetaceans; Seabirds; Seals; Large pelagics; Mesopelagics; Sardine; Anchovy; Juvenile horse; Adult horse mac; Small M. capens\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Guinea (1998)}, $\rho = 0.223753$} \\
\hline
Benthos; Zool S; Zool L; Crustacés; Céphalopodes; Côtier pel S inv; Côtier S inv; Mulets; Dem L inv; Pel S inv; Côtier pel L pred; Pel L pred; Dem M inv; Dem S pred; Disques; Côtier M pred; Bars; Sélaciens L côtiers; Thons mineurs; Sélaciens L prof; Côtier L pred; Dem L pred; Producteurs primaires; Sélaciens M côtiers; Sélaciens M prof; Dem S inv; Mésopélagiques; Ethmalose; Côtier M inv; Bathy SM inv; Mâchoiron; Bathy S pred; Dauphins; Bathy L pred; Oiseaux; Capitaine royal; Dem M pred; Tortues; Côtier S pred; Petit capitaine; Baleines; Gros capitaine; Thons majeurs\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern Gulf St Lawrence (1985)}, $\rho = 0.223034$} \\
\hline
Echinoderms; Molluscs; Other ben. inver.; Small zooplankton; Large zooplankton; Shrimp; Polychaetes; Sand lance; Small demersals; Redfish; American plaice; Skates; Small Green. halibut; Large crustacea; Capelin; Small cod; Flounders; Plank. small pelagics; Pisci. small pelagics; Large pelagics; Large cod; Large demersals; Arctic cod; Large Green. halibut; Phytoplankton; Cetacea; Seabirds; Harbour seals; Harp seals; Grey seals; Hooded seals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Greenland, West Coast (1997)}, $\rho = 0.222550$} \\
\hline
Small Zooplankton; Large Zooplankton; Benthos; Other bot fish; Northern shrimp; Long rough Dab; Thorny ray; Grl. halibut juv; Other pel fish; Squids; Redfish juv less 15cm; Polar cod; Redfish larger than 14cm; Cod juv; Toothed whales; Phytoplankton; Baleen whales; Seabirds; Cod 4+; Grl. halibut 5+; Seals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{South East Alaska (1963)}, $\rho = 0.222404$} \\
\hline
Benthic inverts; L zoo; Epibenthic carnivorous; Shrimps; Sablefish; Deep S; Dem S; Pollock juv; Arrowtooth; Flatfish; Pollock adult; Baleen whales; Rockfish slope; Rockfish shelf; Halibut; Shark and skate; Birds; Dem L; S zoo; Shark mammal eater; Cephalopods; Deep L; Transient orca; Pel S; Salmon; Pacific cod; Pel L; Herring; POP; Sandlance; Marine plants; Phyto; Sea lions embryo; Sea lions pup; Sea otters; Small mammals; Sea lions adults; Sea lions juv; Toothed whales\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Barnegat Bay (1981)}, $\rho = 0.222275$} \\
\hline
Benthic infauna/epifauna; Bay anchovy; Amphipods; Hard clams; Oyster; Non-piscivorous seabirds; Atlantic Menhaden; Mummichog; Blue crabs; Winter flounder; Atlantic silversides; Spot; River herring; Copepods; Bluefish; Summer flounder; Microzooplankton; Atlantic Croaker; Weakfish; Ctenophores; Striped bass; Benthic algae; Phytoplantkon; SAV; Sea nettles; Piscivorous seabirds\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Gulf of Carpentaria (1990)}, $\rho = 0.221083$} \\
\hline
Small crustaceans; Microbial heterotrophs; Zooplankton; Echinoids; Bivalves; Ophioroids; Holothurians; Worms; Meiofauna; Sessile epibenthos; Small gastropods; All other non-commercial prawns; Small jellies; Ichthyoplankton; Asteriods; Large jellies; Turtles; Spatangoids; Other large crabs; Sand crab; Stomatopods; Sardines and pilchards; Whitings, goatfishes and flounders; Ponyfishes, pinkies and trumpters; Small tunas and bonitos; Lizardfishes; Octopus; Pelagic scads; The mud crab; All other commercial prawns; Thallasinid prawns (Callianassa); Catfish and flatheads; Dolphins; Large trevallies and barracudas; Sweetlips and grunters; Silver biddies and small catfishes; Large mackerels and tunas; Slipper lobsters; Cobia, groupers and jacks; Red snappers; Black-tip sharks; Jewfishes; Rock lobster; Forams; Squid and cuttlefishes; Banana prawn adult; Garfishes, rabbitfishes and batfishes; Small rays; Seagrass; Tiger prawn adult; Mullets; Large gastropods; Banana prawn subadults; Mangroves; Microphytobenthos; Medium coastal sharks; Phytoplankton; Macroalgae; Dugongs; Insects; Tiger prawn subadults; Benthic shark / rays; Common terns; Crested terns; Brown boobies; Lesser frigates; Sea snakes; Manta rays; Tiger prawn juvenile; Banana prawn juvenile; Large rays; Eagle rays; Small sharks; Sawfishes; Billfishes; Weasel sharks; Large sharks; Reef sharks; Crocodiles\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sri Lanka (2000)}, $\rho = 0.220838$} \\
\hline
zooplankton; zoobenthos; molluscs; crabs; annelids; shrimps; mugilids; bigeye scad; milk fish ; thrissa spp; other clupeids; drums; ponyfishes; other carangids; ribbonfish; sea cat fish; Large tunas; false trevallie; needlefish; medium tunas; yellowstripe; phytoplankton; small barracudas; dolphinfishes; pomfrets, torps; large barracudas; wolf herrings; small tunas; phytobenthos; cephalopods; halfbeaks; flying fishes; herrings; sardines; anchovies; terapontids; indian mackerel; soles\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{River Rheido, Wales}, $\rho = 0.220407$} \\
\hline
 Rhithrogena;  Baetis;  Chironomidae;  Leuctra, Protonemeura, Amphinemura;  Oligochaeta;  CoperwcIa, Cladocera;  Hydropsyche;  Chloroperla;  Simulium;  Isoperla;  Dystiscidae (Deronectes, Oreonectes);  Polycentropus;  green algae;  agmented leaf, stem tissue, moss;  diatoms;  Batrachospermum, Lemanea;  Perlodes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Paraná River Floodplain (1992)}, $\rho = 0.220000$} \\
\hline
Insects; Zooplankton; Astyanax altiparanae; Other benthos feeders; Benthos; Hypostomus spp; Cyphocharax modesta; Steindacchnerina insculpta; Prochilodus lineatus; Acestrorhyncus lacustris; Other detritus feeders; Loricariichthys platymetopon; Pterodoras granulosus; Leporinus obtusidens; Other omnivores; Plagioscion squamisissimus; Pseudoplatystoma corruscans; P maculatus; Trachydoras paraguayensis; Leporinus friderici; Hoplosternum littorale; Iheringichthys labrosus; Aquatic macrophytes; Phytoplankton; Other insectivores; Other piscivores; Serrasalmus marginatus; Rhaphiodon vulpinis; Salminus brasiliensis; Serrasalmus spiloptera; Brycon orbignyanus; Hoplias malabaricus; Periphyton; Schizodon altoparanae; Schizodon borelii; Parauchenipterus galeatus; Hypophthalmus edentatus; Auchenipterus nuchalis; Hemisorubin platyrhynchos\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Sierra Leone (1964)}, $\rho = 0.218468$} \\
\hline
Carnivorous zooplankton; Herbivorous zooplankton; Benthos; Mullets and other herbivores; Sardinellas; Scads and mackerels; Crustaceans; Small pelagic invert feeders; Small demersal predators; Small demersal invert feeders; Medium demersal invert feeders; Large demersal predators; Sickle-and spadefish; Jacks; Croackers; Cephalopods; Large pelagic predators; Large demersal invert feeders; Bongo shad; L Coastal Sharks and Rays; L Deep Sharks and Rays; Large Tuna; M Coastal Sharks and Rays; Mesopelagics; M Deep Sharks and Rays; Catfish; Small Bathypelagic predators; SM Bathydem invert feeders; Royal Threadfin; M Bathypelagic invert feeders; Small pelagic predators; Lesser African Threadfin; Primary producers; Turtles; Seabirds; Medium demersal predators; Baleen whales; Large Bathypelagic predators; Gaint African Threadfin; Groupers; Small Tuna; Large Bathydem predators; Toothed whales and dolphins\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Ningaloo (2007)}, $\rho = 0.217195$} \\
\hline
Adult Turtles; Dugongs; Urchins; Benthos; Herbivores; Zooplankton; Small reef fish; Squid; Manta Rays; Sm Coral; Lobster; Shells; Lg Coral; Kingprawn; Crabs; Octopus; Bananaprawn; Demersal sharks; Shallow demersal fish; Hatchlings; Foxes; Saurids; Lethrinids juv; Whales; Dolphins; Pelagic sharks; Ospreys; Queenfish; Serranids; Small lutjanids; Reef Associated Pelagics; Small pelagics; Mackerels; Tuskfish; Trevallies; Coastal seabird; Nemipterids; Buffell grass; Native grass; Phytoplankton; Lethrinids adults; Coral Spawn; Macrophytes; Goats and sheep; Marsupial grazers; Whale sharks; Turtle eggs; L nebulosus juv; Tuna and billfish; L nebulosus adult\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Mount St Michel Bay (2003)}, $\rho = 0.216561$} \\
\hline
juvenile cephal; juvéniles poiss; Moules; macrobenthos; Mulets; huîtres2; huîtres; petites espèces; Macrobenthos2; poissons adulte; gros crustacés; zooplancton her; Meiobenthos; Crepidule; Macrophytes; phoques; Phytobenthos1; mouton; phytobenthos 2; Phytoplancton; anatidés; oiseaux limicol; céphalopodes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Azores (1997)}, $\rho = 0.216027$} \\
\hline
Small Zooplankton; Benthic filter feeders; Other benthos; Benthic worms; Crabs; Large Zooplankton; Shrimp; Demersal S; Cephalopods; Mesopelagics; Pelagic M; Shallow water S; Shallow water M; DW sharks; Pelagic S; Pelagic sharks; Rays and other sharks; H. dactylopterus; Bahtydemersal L; Beryx decadactylus; Toothed whales; Conger conger; Pelagic L; Bathydemersal S; Shallow water L; Demersal M; Algae; Bathydemersal M; Bathypelagic; Pagellus bogaraveo; Demersal L; Lepidopus caudatus; Phytoplankton; Pagrus pagrus; Baleen whales; Turtles; Beryx splendens; Pontinus kuhlii; Phycis phycis; Tunas; Seabirds; Raja clavata; Mora moro; Dolphins\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Icelandic shelf (1997)}, $\rho = 0.215079$} \\
\hline
Benthos; Nothern shrimp; Other flatfish; Nephros; Molluscs; Grrenland halibut; Other dem fish; Saithe; Nekton; Seabirds; Redfish; Cod; Phytoplankton; Zooplankton; Marine mammals; Capelin; Other pelagics; Herring; Juvenile cod; Haddock\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Australia North West Shelf (1986)}, $\rho = 0.215019$} \\
\hline
LgZooplankton; SmZooplankton; Megabenthos; Macrofauna; SmallPelagics; SessEpibenthos; DpPonyfish; ComPrawns; ShTriggerFish; JuvCarangids; ShLutjanids; ShSmFish; ShMedFish; ShLizard; DpSmFish; ShNemipterirds; ShLgFish; Squid; DpLizard; ShSerranids; ShMullidae; ShLethrinids; DpMedFish; DpLgFish; DpNemipterids; Coastal sharks; BenPhytoplankton; Microphytobenthos; PelPhytoplankton; Rays; RedEmperor; ShSweetlip; DpMullidae; SmTunas; AdCarangids; FryPBream\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bay of Biscay (1980)}, $\rho = 0.214697$} \\
\hline
Bacteria; Surface suspension and deposit feeders; Subsurface deposit feeders invertebrates; Shrimps; Benthic meiofauna; Suprabenthic invertebrates; Microzooplankton; Mesozooplankton; Demersal S; Carnivorous and necrophagous benthic invertebrates; Lobsters/Crabs; Demersal M; Demersal L; Whitting; Norway lobster; Sharks/rays; Macrozooplankton; Sharks L; Sardine; Cephalopods; Hake adulte; Toothed whales; Anchovy; Pouts; Pelagic M; Horse mackerel; Mackerel; Anglerfish; Blue whitting; Pelagic L; Sole; Surface feeders seabirds; Plunge and pursuit divers seabirds; Benthic producers ; Phytoplankton L; Phytoplankton S; Plaice; Baleen whales; Hake juvenile; Megrim; Sea bass\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bay of Biscay (2013)}, $\rho = 0.214658$} \\
\hline
Bacteria; Surface suspension and deposit feeders; Subsurface deposit feeders invertebrates; Shrimps; Benthic meiofauna; Suprabenthic invertebrates; Microzooplankton; Mesozooplankton; Demersal S; Carnivorous and necrophagous benthic invertebrates; Lobsters/Crabs; Demersal M; Demersal L; Whitting; Norway lobster; Sharks/rays; Macrozooplankton; Sharks L; Sardine; Cephalopods; Hake adulte; Toothed whales; Anchovy; Pouts; Pelagic M; Horse mackerel; Mackerel; Blue whitting; Sole; Hake juv; Pelagic L; Surface feeders seabirds; Plunge and pursuit divers seabirds; Benthic producers ; Phytoplankton L; Phytoplankton S; Plaice; Baleen whales; Megrim; Sea bass; Anglerfish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Tasmanian Seamounts Marine Reserve (1992)}, $\rho = 0.209733$} \\
\hline
Zooplankton; Gelatinous zooplankton; Benthopelagic fish; Megabenthos; Epibenthos; Infauna; Corals; Pelagic crustaceans; Small squid; Scavengers; Demersal sharks; Pelagic sharks; Shallow migratory small fish; Deep migratory small fish; Non-migratory small fish; Lge squid; Lge pelagic fishes; Phytoplankton; Benthic fish; Alepocephalids; Other oreos; Roughy; Warty oreo; Tunas  billfishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Lake Paajarvi, littoral zone, Finland}, $\rho = 0.209547$} \\
\hline
bacterioplankton; Copepoda; Mollusca; Anodonta; Nematoda; Asellus; Ephemeroptera; Chironomidae - Microtendipes; Sida; Perea; Asplanchna, Polyphemus; Acanthocyclops; Chironomidae - Procladius; Rutilus rutilus; terrestrial adult insects; phytoplankton; Potamogeton, Lobelia, lsoetes, Sparganiwn; Hirudinea; Mermithidae; Trichoptera; Turbellaria; salakka; Gymnocephalus cemus; Perca fluviatilis; Coregonus lavaretus\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Port Phillip Bay (1994)}, $\rho = 0.209080$} \\
\hline
Large zooplankton; Deposit Feeders; Filter Feeders; Epi. Predators; Other Grazers; Mullet and Garfish; Scavengers; Scallops and mussels; Juvenile Mullet; Rays; Snapper; Clupeoids; Juvenile Snapper; Abalone; Birds; Other demersals; Southern calamari; Flatfish; Juvenile Flatfish; Inf. Predators; Sharks; Other cepahalopods; Piscivores; Juvenile Piscivores; Small zooplankton; Marine mammals; Macroalgae; Microphytobenthos; Phytoplankton; Seagrass; KG Whiting; Juvenile KG Whiting; Sth Rock Lobster\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Eastern Corsican Coast (2012)}, $\rho = 0.208329$} \\
\hline
Worms; Benthic crustaceans; Echinoderms; Cnidaria; Zooplankton; Shrimps; Bivalvia; Gelatinous; European lobster; Spiny lobster; Piscivorous fish; Benthic cephalopods; Suprabenthic cephalopods; Seriola; Planktivorous fish; BIF; Gasteropods; Sparidae; E. marginatus; Labridae; SIF; Purple sea urchin; European Shag; Rays; Sea grass; Chromis chromis; Macroalgae; Mullus surmuletus; Phytobenthos; Phytoplankton; Sarpa salpa; Sciaena umbra; Serranidae; Benthic sharks; Scorpaena scrofa; Bottlenose dolphin; Dentex dentex; Sphyranidae\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Celtic Sea-Biscay (1980)}, $\rho = 0.206689$} \\
\hline
Zooplankton S; Benthos; Zooplankton L; Shrimps/crabs; Lobsters/crabs; Cephalopods; Demersal M; Demersal L; Whiting; Cod; Pouts; sharks/rays; Demersal S; Sharks L; Herring; Mackerel; Hake; Hake juv; Monkfish; Bathy M; Sprat; Pelagic L; Bathy S; Toothed whales; Horse mackerel; Bathy L; Anchovy; Pelagic M; Blue whiting; Benthic producers; Phytoplankton; Sardine; Plaice; Sole; Baleen whales; Cod juv; Megrim\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Celtic Sea-Biscay (2012)}, $\rho = 0.206689$} \\
\hline
Zooplankton S; Benthos; Zooplankton L; Shrimps/crabs; Lobsters/crabs; Cephalopods; Demersal M; Demersal L; Whiting; Cod; Pouts; sharks/rays; Demersal S; Sharks L; Herring; Mackerel; Hake; Hake juv; Monkfish; Bathy M; Sprat; Pelagic L; Bathy S; Toothed whales; Horse mackerel; Bathy L; Anchovy; Pelagic M; Blue whiting; Benthic producers; Phytoplankton; Sardine; Plaice; Sole; Baleen whales; Cod juv; Megrim\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{USA, Mid Atlantic Bight (1995)}, $\rho = 0.205308$} \\
\hline
Bivalves; Small crustaceans; Polychaetes; Euphausiids; Sessile epibenthos; Jellies; Echonoderms; Shrimp; Spot; Forage fish; Crabs; Lobsters; Demersal invertebrate eaters; Demersal piscivores; Benthic piscivores; Stomatopods; Snapper / grouper; Flounders; Mysids; Rays and skates; Ocean pout; Drum / croaker; Spiny dogfish; Macrozooplankton; Microzooplankton; Cods and hakes; Squid; Coastal sharks; Goosefish; Tunas; Atlantic menhaden; Med. pel. pisc (Mackerel); Striped bass; Billfishes; Seals; Butterfishes; Benthic invertebrate eaters; Demersal planktivores; Atlantic salmon; Large pelagic planktivores; Bluefish; Macrophytes; Microphytobenthos; Phytoplankton; Scup; Tilefish; Redfish; Octopods; Black seabass; Jacks; Baleen whales; Weakfish; Marine birds; Dolphins and porpoise\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Bay of Biscay (1994)}, $\rho = 0.204753$} \\
\hline
Mesozooplankton; Microzooplankton; Bacteria; Benthic meiofauna; Necrophagous benthic invertebrates; Surface suspension and deposit feeders inv; Sub-surface deposit feeders invertebrates; Carnivorous benthic invertebrates; Benthivorous demersal fish; Piscivorous and benthivorous demersal fish; Suprabenthivorous demersal fish; Pelagic cephalopods; Horse mackerel; Mackerel; Benthic cephalopods; Sardine; Piscivorous demersal fish; Anchovy; Macrozooplankton; Sprat; Large phytoplankton; Surface feeders seabirds; Pursuit divers seabirds; Small phytoplankton; Suprabenthic invertebrates; Common dolphins; Long-finned pilot whales; Harbour porpoises; Striped dolphins; Bottlenose dolphins\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Celtic Sea (2013)}, $\rho = 0.203465$} \\
\hline
Bacteria; Surface suspension and deposit feeders; Sub-surface deposit feeders invertebrates; Shrimps; Benthic meiofauna; Suprabenthic invertebrates; Microzooplankton; Mesozooplankton; Carnivorous and necrophagous invertebrates; Lobsters/Crabs; Demersal L; Whitting; Cod ad; Haddock; Norway lobster; Sharks/rays; Sharks L; Cephalopods; Macrozooplankton; Demersal S; Hake juvenile; Toothed whales; Hake adulte; Anglerfish; Mackerel; Pelagic L; Herring; Sprat; Demersal M; Sardine; Pouts; Pelagic M; Boarfish; Horse Mackerel; Sole; Surface feeders seabirds; Plunge and pursuit divers seabirds; Blue whitting; Benthic producers; Phytoplankton L; Phytoplankton S; Plaice; Baleen whales; Cod juvenile; Megrim; Sea bass\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Jurien Bay (2007)}, $\rho = 0.202384$} \\
\hline
Small Zooplankton; Small mobil epifauna; Chaetognaths; Large Herb. Gastropods; Inshore reef ass. herbivore; Microbial heterotrophs; Large mobile herb. invert.; NDR sand ass. omnivore; Photo. corals/sponges; Sessile bivalves; Roe abalone; Small Gastropods; Infaunal bivalves; Infauna; Lobster-post puerulus; Deposit feed. invert.; Inshore seagrass ass. zoob. feed.; Small mobile herbivores; Large Crabs; Sessile epibenthos; NDR reef ass. omnivore; Lobster- Juvenile; Lobster - Adolescent; Octopus; NDR reef ass. zoobenthos feed.; Inshore reef ass. zoobenthos feed.; NDR pelagic zooplankton Feed.; Inshore seagrass ass. omnivore; Inshore reef ass. omnivore; NDR sand ass. zoobenthos feed.; Large mobile carn. invert.; NDR seagrass ass. omnivore; Rays; Pink snapper; Inshore ass. carnivore; Lobster Adult; Dhufish; Large coastal sharks; Large Zooplankton; Cuttlefish; NDR reef ass. herbivore; Squid; Inshore sand ass. omnivore; Small coastal sharks; Baldchin grouper; Sea turtles; King wrasse; Inshore pelagic zooplankton feed; Large Carn. Gastropods; NDR reef aa. zooplankton feed; Small Phytoplankton; Ecklonia; Sargassum; Large Phytoplankton; Western foxfish; Perenial seagrasses; Corraline algae; Microphytobenthos; Ephemeral seagrasses; Turfs; Low algae; Seagrass epiphytes; Carnivorous Jellyfish; Intertidal birds; NDR seagrass ass. carnivore; Inshore benthopelagic carnivore; Breaksea cod; NDR reef ass. carnivore; NDR sand ass. carnivore; Surface diving birds; NDR benthopelagic carnivore; Sea lions; Dolphins\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Cerbère-Banyuls MPA (2013)}, $\rho = 0.202074$} \\
\hline
Meso and microzooplankton; Macrozooplankton; Other macro-benthos; Suprabenthos; Other sea urchin; Purple sea urchin; Sea cucumbers; Bivalves; Gastropods; Benthopelagic cephalopods; Non-commmercial decapods; No commercial small demersal fish; Labridae and Serranidae; Other commercial decapods; Coastal benthic cephalopods; Other medium pelagic fishes; Flatfishes; Mugilidae; Other corals and gorgonians; Red coral; Sparidae; Common two-banded seabream; White seabream; Other commercial medium demersal fish; Brown meagre; No commercial medium demersal fish; European hake; European conger; Anglerfish; Horse mackerels; Mackerels; European sardine; Other benthic cephalopods; Salema; Common pandora; Other large pelagic fishes; European anchovy; Other small pelagic fish; Jellyfish; Salps and other gelatinous zooplankton; Scorpaenidae; Red mullet; European lobster; Surmulet; Poor cod; Red scorpionfish; Rays and skates; Terns; Endangered and pelagic seabirds; Gulls and cormorants; Striped dolphins; Bottlenose dolphins; Large phytoplankton; Mediterranean seagrass; Seaweeds; Small phytoplankton; Loggerhead turtles; Small-spotted catshark; Non-commercial large pelagic fishes; Common dentex; Groupers; Torpedos\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Celtic Sea (1980)}, $\rho = 0.201644$} \\
\hline
Bacteria; Surface suspension and deposit feeders; Sub-surface deposit feeders invertebrates; Shrimps; Benthic meiofauna; Suprabenthic invertebrates; Microzooplankton; Mesozooplankton; Carnivorous and necrophagous invertebrates; Lobsters/Crabs; Demersal L; Whitting; Haddock; Cod ad; Norway lobster; Sharks/rays; Sharks L; Macrozooplankton; Demersal S; Cephalopods; Hake adulte; Anglerfish; Hake juvenile; Pelagic L; Mackerel; Toothed whales; Pouts; Horse Mackerel; Pelagic M; Herring; Demersal M; Sardine; Sprat; Sole; Blue whitting; Cod juvenile; Surface feeders seabirds; Plunge and pursuit divers seabirds; Benthic producers; Phytoplankton L; Phytoplankton S; Plaice; Boarfish; Baleen whales; Megrim; Sea bass\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Iceland (1950)}, $\rho = 0.200785$} \\
\hline
Benthos; Northern Shrimp; Nephrops; Molluscs; Baleen whales; Other Dem. Fish; Saithe; Seabirds; Other Fish; Redfish; Adult Cod; Pinnipeds; Toothed whales; Phytoplankton; Zooplankton; Greenland Halibut; Other Flatfish; Other Pelagics; Capelin; Benthic producers; Herring; Juvenile Cod; Haddock\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Azores archipelago (1997)}, $\rho = 0.200377$} \\
\hline
large zoopl; small zoopl; other benthos; sea stars; coastal M herb; shrimps crabs; Loligo; lobsters; demersal M pred; pelagic M pred; demersal M inv; demersal L pred; cephalop s; coastal L pred; Dolphins; coastal S inv; coastal S pred; coastal M inv; pelagic S pred; coastal M pred; pelagic S inv; deepwater S; mesopelagics; demersal S inv; sharks L; deepwater M; Phycis phycis; cephalop L; macrophytes; phytoplankton; rays; pelagic L pred; coastal S herb; Octopus; Helicolenus; tunas; sharks M; baleen whales; Pagellus bogaraveo; birds; deepwater L; killer whales; turtles\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Baie de Seine (2000)}, $\rho = 0.198924$} \\
\hline
Meszooplankton and Macrozooplancton; Suprabenthos; Bacteria; Benthic inv. deposit feeders (Subsurface); King scallop; Meiofauna; Benthic inv. bivalves filter feeders; Benthic inv. deposit feeders (Surface); Benthic inv. predators; Benthic inv. filter feeders; Fish piscivorous; Benthopelagic cephalopods; Fish benthos feeders; Microzooplankton; Fish planctivorous; Fish atlantic horse mackerel; Fish sharks; Benthic cephalopods; Fish atlantic cod; Fish european pilchard; Fish european sprat; Fish whiting; Harbour porpoises; Bottlenose dolphins; Phocidae; Fish mackerel; Discards; Fish rays; Phytoplancton; Fish sole; Fish limande ; Fish sea bream; Fish european plaice; Benthic feeders seabirds; Fish flounder; Fish gurnard; Fish poor cod; Fish pouting; Fish european seabass; Plunge and pursuit divers seabirds; Surface feeders seabirds\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Sea (1974)}, $\rho = 0.198148$} \\
\hline
Polychaetes; Echinoderms; Copepods; O.crustaceans; O.invertebrates; Whiting; Dab; O.macrobenthos; Herring; Gurnards; Juv. cod; Juv. whiting; Euphausiids; Sandeel; Norway pout; Juv. haddock; Sprat; Seals; Haddock; Cod; Phytoplankton; Sole; Plaice; Juv. saithe; Horsemackerel; Mackerel; Raja; O. predators; Birds; West mackerel; Saithe\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Ria-Lake Tapajos (2013)}, $\rho = 0.196423$} \\
\hline
Zooplankton; Aquatic invertebrates; Others algivores/detritivores; Semaprochilodus spp. ; Schizodon spp.; Laemolyta spp.; Loricariichthys spp.; Mesonauta festivus; Geophagus spp.; Acarichthys heckelii; Satanoperca acuticeps; Hemiodus spp.; Others piscivores; Igapo Forest; Acaronia nassa; Plagioscion squamosissimus; Pellona castelnaeana; River dolphins; Terrestrial invertebrates; Cichla spp.; Otters; Arapaima gigas; Brachyplatystoma rousseauxii; Brachyplatystoma filamentosum; Periphyton; Phytoplankton; Others frugivores; Pacu; Colossoma macropomum; Turtles; Bryconops spp.; Leporinus spp.; Hypophthalmus marginatus; Others invertivores\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Gulf of Gabes (2000)}, $\rho = 0.193932$} \\
\hline
Micro and mesozooplankton; Amphipoda and Isopoda; Polychaetes; Benthic molluscs; Foraminifera; Echinoderms; Invertebrate suspension feeders ; Crabs; Mullets; Benthic cephalopods; Mantis shrimp; Benthopelagic cephalopods; Macro-carnivorous Fish (1); Sharks; Macrozooplankton; Medium pelagic fish; Macro-carnivorous Fish (2); Small tuna ; Sea birds; Rays (2) ; Rays (1); Piscivorous Fish; Atlantic bluefin tuna; Sparidae; Dolphins; Benthic invertebrate feeders (2); Macro-algae; Alien shrimps ; Benthic invertebrate feeders (1); Horse mackerel; Phytoplankton; Picarel; Deep shrimps ; Caramote prawn; Posidonia oceanica; European anchovy; European pilchard; Round sardinella; Bogue\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Apalachicola Bay (2000)}, $\rho = 0.192937$} \\
\hline
Macrozooplankton; Microzooplankton; Zoobenthos; Blue crab; Oysters; Atlantic bumper; Mullet; Arrow shrimp; Adult white shrimp; Pink shrimp; Brown shrimp; Roughback shrimp; Brief squid; Adult spot; Juvenile pigfish; Juvenile spot; Juvenile silver perch; Hogchoker; Juvenile Atlantic croaker; Red drum; Adult sand seatrout; Adult pigfish; Adult Atlantic croaker; Large coastal sharks; Snapper; Dolphins; Southern kingfish; Small coastal sharks; Adult silver perch; Seabirds; Adult hardhead catfish; Inshore lizardfish; Seagrass; Juvenile white shrimp; Adult bay anchovy; Phytoplankton; Adult pinfish; Menhaden; Mojarra; Juvenile bay anchovy; Juvenile striped anchovy; Sardines; Menidia silversides; Adult striped anchovy; Gulf butterfish; Juvenile pinfish; Fringed flounder; Gulf flounder; Black drum; Juvenile sand seatrout; Juvenile hardhead catfish; Atlantic stingray; Mantis shrimp\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Denmark, Faroe Islands (1997)}, $\rho = 0.191579$} \\
\hline
Benthos; Other demersal fish; Other deep water; Greenland Halibut; Saithe; Seabirds; Sm. Zooplankton; Lrg. Zooplankton; Nekton; Toothed mammals; Other pelagics; Herring; Blue Whiting; Haddock; Mackerel; Redfish; Phytoplankton; Baleen whales; Cod\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Lake Michigan}, $\rho = 0.190600$} \\
\hline
Rotifers; Cladocerans; Cyclopoids; Sphae/Gast; Benthic microin; Diporeia; Mysis; Other fish; Oligoch/Chiron; Calanoids; Leptodora; Alewife; Rainbow smelt; Bloater; Slimy sculpin; Deepwater sculp; Sea lamprey; Juv. Lake Trout; Flagellates; Blue-greenGree; Diatoms; Lake Whitefish; Yellow perch; Burbot; Coho; Juv. Brown trou; Juv. Chinook; Juv. Steelhead; Brown trout; Steelhead; Lake trout; Chinook; Juv. Coho\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Gulf of Thailande (1963)}, $\rho = 0.186385$} \\
\hline
Zooplankton; Scad; Benthos; O.fish; Shrimps; Sm.dem.benth.; Med.dem.benth.; Flatfish; Crab, lobster; Rays; Tuna; Cephalopods; Phytoplankton; Sharks; M. mammals; Mackerel; Sm. pelagics; Med.dem.pisc.; Ponyfishes; Sm.dem.pisc.; Molluscs; Jellyfish; Juv.Lg.Pisciv.; Juv. sharks; Juv. groupers; Lg. piscivores; Grouper/snapper; Scomberomorus\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North Sea (1981)}, $\rho = 0.186258$} \\
\hline
PT pico; Polychaeta; Echinodermata; O.macrobenthos; O.invertebrates; O.crustaceans; Copepoda; O.prey fish; Cod; Whiting; Haddock; Juvenile fish; Mackerel; Saithe; PT nano; Euphausiacea; PS nano; Sandeel; PS micro; PS pico; PT micro; Sole; Plaice; Sprat; Ray; Norway pout; O.pred.fish; Herring\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Lower Chesapeake Bay}, $\rho = 0.183984$} \\
\hline
Free Bacteria; Ctenophores; Particle Attached Bacteria; Benthic Bacteria; Suspension Feeding Benthos; Menhaden; Meiofauna; Deposit Feeding Benthos; Bay anchovy; Blue Crab; Meroplankton; Mesozooplankton; Ciliates; Spot; Net Phytoplankton; Croaker; Picoplankton; Heteroflagellates; Hogchoker; Striped Bass; Weakfish; Bluefish; Microphytobenthos; SAV; Rotifers; Chrysaora\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Gulf of Mexico (1950)}, $\rho = 0.183215$} \\
\hline
18+ Mullet; Benthic Invertebrates; Macro Zooplankton; Shrimp; Caridan Shrimp; Catfish; Lobster; Stone Crab; juv Menhaden; Menhaden; Pin Fish; Small fish; Bay Anchovy; 0-6 Mullet; 6-18 Mullet; Blue Crab; 0-3 Red Drum; 3-8 Red Drum; Micro Zoolplankton; Silver Perch; Pigfish; Scaled Sardine; Jacks; Infauna; Atlantic croaker; 3-18 Sea Trout; Rays; 18+ Sea Trout; Attached Microalgae; Phytoplankton; Sea Grass; red snapper 0-6; Grouper 0; 0-3 Sea Trout; Pompano; red snapper 6-24; Mackrel 0-3; Ladyfish 0-10; Ladyfish 10+; Grouper 1-3; 8-18 Red Drum; 36+ Red Drum; 18-36 Red Drum; red snapper older; Grouper 3+; Mackrel 3+; LCsharks\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Florida Bay - wet season}, $\rho = 0.182947$} \\
\hline
Benthic Flagellates; Herbivorous Amphipods; Detritivorous Gastropods; Water Flagellates; Halfbeaks; Sponges; Bivalves; Suspension Feeding Polych; Manatee; Mullet; Meiofauna; Detritivorous Polychaetes; Detritivorous Crabs; Omnivorous Crabs; Pink Shrimp; Herbivorous Ducks; Echinoderma; Benthic Ciliates; Macrobenthos; Detritivorous Amphipods; Benthic Crustaceans; Predatory Gastropods; Predatory Shrimp; Predatory Polychaetes; Coral; Other Cnidaridae; Callinectus sapidus; Predatory Crabs; Catfish; Other Copepoda; Acartia Tonsa; Oithona nana; Paracalanus; Other Zooplankton; Meroplankton; Eels; Isopods; Other Demersal Fishes; Pinfish; Herbivorous Shrimp; Sailfin Molly; Rainwater killifish; Other Killifish; Water Cilitaes; Parrotfish; Epiphytes; Thor Floridanus; Epiphytic Gastropods; Raptors; Crocodiles; Goldspotted killifish; Other Pelagic Fishes; Code Goby; Clown Goby; Blennies; Bay Anchovy; Free Bacteria; Mojarra; Sardines; Lobster; Barracuda; Flatfish; Gulf Pipefish; Silverside; Dwarf Seahorse; Other Horsefish; Toadfish; Anchovy; Puffer; Dolphin; Grunt; Filefishes; Needlefish; Scianids; Other Snapper; Lizardfish; Stone Crab; Brotalus; Thalassia; Halodule; Syringodium; Spotted Seatrout; Drift Algae; Porgy; Green Turtle; Omnivorous Ducks; Hawksbill Turtle; Bonefish; Pompano; Rays; Loggerhead Turtle; Red Drum; Spadefish; Small Shorebirds; Gruiformes; Gray Snapper; Gulls \& Terns; Snook; Grouper; Tarpon; Jacks; Ibis; Small Herons \& Egrets; Roseate Spoonbill; Big Herons \& Egrets; Kingfisher; Greeb; Predatory Ducks; Loon; Comorant; Pelican; Sharks; Mackerel; 2um Spherical Phytoplankt; Synedococcus; Oscillatoria; Small Diatoms (<20um); Big Diatoms (>20um); Dinoflagellates; Other Phytoplankton; Benthic Phytoplankton; Roots\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Florida Bay (2006)}, $\rho = 0.182928$} \\
\hline
Caridean shrimp; Small crustaceans; Bivalves; Annelids; Mud crabs; Gastropods; Sessile epibenthos; Mullet; Portunid crab; Echinoderm; Pink shrimp; Lobster; Gulf toadfish; Pinfish; Sheepshead minnow; Rainwater killifish; Mojarras; Clown goby; Mesozooplankton; Spider crabs; Hardhead catfish; Lemon shark; Clupeids; Goldspotted killifish; Hardhead silverside; Bay anchovy; Bonnethead shark; Phytoplankton; Red drum; Spotted seatrout; Macroalgae; Seagrass; Sheepshead; Grunts; Redfin needlefish; Octopods; Epiphytes; Hardhead halfbeak; Microzooplankton; Common snook; Crevalle jack; Gray snapper; Atlantic tarpon; Great barracuda; Seabirds\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Everglades Graminoids}, $\rho = 0.182405$} \\
\hline
Mesoinverts; Terrestrial Inverts; Fishing spider; Passerines; Mink; Living Sediments; Living POC; Other Macroinverts; Crayfish; Tadpoles; Turtles; Flagfish; Opossum; Gruiformes; Poecilids; Ducks; Mosquitofishes; Other Small Fishes; Chubsuckers; Bluefin killifish; Killifishes; Shiners \& Minnows; Other Centrarchids; Catfish; Large Aquatic Insects; Alligators; Freshwater Prawn; Apple snail; Raccoons; Rats\&Mice; Otter; Snakes; Grebes; Gar; Macrophytes; Topminnows; Floating Veg.; Bitterns; Periphyton; Bobcat; Panthers; Pigmy Sunfish; Bluespotted Sunfish; Utricularia; Small frogs; Medium frogs; Salamanders; Muskrats; Rabbits; W-T Deer; CSSsparrow; Salamander larvae; Nighthawks; Dollar Sunfish; Snailkites; Redear Sunfish; Spotted sunfish; Warmouth; Cichlids; Largemouth Bass; Other Large Fishes; Large frogs; Lizards\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Tampa Bay (1950)}, $\rho = 0.181945$} \\
\hline
Benthic Invertebrates; Macro Zooplankton; Caridan Shrimp; Catfish; Bay Anchovy; 18+ Mullet; Stone Crab; Shrimp; Pin Fish; Blue Crab; Spot; Menidia (silverside); 0-6 Mullet; 0-3 Red Drum; Micro Zoolplankton; Manhaden; 6-18 Mullet; 3-12 Snook; Bumper; 3-8 Red Drum; 0-12 Snook; Silver Perch; Pigfish; Jacks; 3-18 Sea Trout; Mojarra; Cyprinodontids; Poecilids; Threadfin Herring; Scaled Sardine; 3-12 Sand Trout; Gobies; Infauna; 90+ Snook; Ladyfish 0-10; 18+ Sea Trout; Attached Microalgae; Phytoplankton; Sea Grass; Rays; 0-3 Sand Trout; 0-3 Sea Trout; Mackrel 0-3; Ladyfish 10+; 12-48 Snook; 36+ Red Drum; 18-36 Red Drum; 8-18 Red Drum; 12+ Sand Trout; 48-90 Snook; Mackrel 3+\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Lesser Antilles (2001)}, $\rho = 0.178564$} \\
\hline
Small zooplankton; Large zooplankton; Small offshore pelagics; Small coastal pelagics; Coastal predators; Other offshore predators; Mackerels; Billfishes; Pelagic sharks; Dolphinfish; Bigeye; Albacore; Large mesopelagics; Small squids; Large squids; Skipjack; Deep-diving whales; Small mesopelagics; Flyingfish; Swordfish; Shallow-diving cetaceans; Wahoo; Blackfin tuna; Phytoplankton; Baleen whales; Yellowfin; Other turtles; Leatherback turtle; Seabirds; Killer whales\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Florida Bay - dry season}, $\rho = 0.178345$} \\
\hline
Benthic Flagellates; Herbivorous Amphipods; Detritivorous Gastropods; Detritivorous Crabs; Water Flagellates; Halfbeaks; Sponges; Manatee; Suspension Feeding Polych; Bivalves; Mullet; Detritivorous Polychaetes; Meiofauna; Omnivorous Crabs; Echinoderma; Pink Shrimp; Herbivorous Ducks; Benthic Ciliates; Macrobenthos; Other Copepoda; Other Zooplankton; Acartia Tonsa; Oithona nana; Paracalanus; Predatory Polychaetes; Benthic Crustaceans; Detritivorous Amphipods; Predatory Shrimp; Meroplankton; Predatory Gastropods; Callinectus sapidus; Predatory Crabs; Catfish; Eels; Other Cnidaridae; Isopods; Other Demersal Fishes; Pinfish; Herbivorous Shrimp; Sailfin Molly; Water Cilitaes; Other Pelagic Fishes; Rainwater killifish; Other Killifish; Epiphytes; Raptors; Crocodiles; Thor Floridanus; Epiphytic Gastropods; Coral; Dolphin; Goldspotted killifish; Code Goby; Barracuda; Clown Goby; Blennies; Bay Anchovy; Mojarra; Free Bacteria; Parrotfish; Sardines; Lobster; Flatfish; Gulf Pipefish; Silverside; Other Horsefish; Dwarf Seahorse; Toadfish; Anchovy; Puffer; Grunt; Filefishes; Needlefish; Other Snapper; Scianids; Lizardfish; Porgy; Brotalus; Stone Crab; Thalassia; Halodule; Syringodium; Spotted Seatrout; Drift Algae; Gray Snapper; Green Turtle; Omnivorous Ducks; Hawksbill Turtle; Bonefish; Pompano; Rays; Loggerhead Turtle; Spadefish; Red Drum; Small Shorebirds; Grouper; Gruiformes; Gulls \& Terns; Snook; Jacks; Tarpon; Sharks; Ibis; Big Herons \& Egrets; Small Herons \& Egrets; Roseate Spoonbill; Kingfisher; Greeb; Predatory Ducks; Loon; Pelican; Comorant; Mackerel; 2um Spherical Phytoplankt; Synedococcus; Oscillatoria; Small Diatoms (<20um); Big Diatoms (>20um); Dinoflagellates; Other Phytoplankton; Benthic Phytoplankton; Roots\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{South Shetlands (1990)}, $\rho = 0.177854$} \\
\hline
Other zooplankton; Salps; Krill; Small invertebrates; Large invertebrates; Other birds; Small demersals; Myctophids; Large demersals; Killer whales; Small pelagics; Small squid; Mackerel icefish; Marbled rockcod; Leopard seals; Large squid; Toothfish; pinguins; Phytoplankton; Minke whales; Crabeater seals; Baleen whales; Anctarctic fur seals; Albatrosses; King pinguins; Weddell and Ross seals; Small cetaceans; Elephant seals; Sperm whales\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Cap de Creus MPA - whole (2008)}, $\rho = 0.176870$} \\
\hline
Meso and microzooplankton; Macrozooplankton; Other macro-benthos; Suprabenthos; Other sea urchin; Purple sea urchin; Sea cucumbers; Bivalves; Gastropods; Non-commmercial decapods; Benthopelagic cephalopods; No commercial small demersal fish; Labridae and serranidae; Sparidae; Other commercial decapods; Other medium pelagic fishes; Flatfishes; Mugilidae; Brown meagre; Other corals and gorgonians; Red coral; Coastal benthic cephalopods; Other commercial medium demersal fish; No commercial medium demersal fish; European hake; European conger; Anglerfish; Horse mackerels; Other large pelagic fishes; Mackerels; European sardine; Other benthic cephalopods; Rays and skates; Common dentex; Gulls and cormorants; Groupers; Torpedos; Common pandora; European anchovy; Jellyfish; Salps and other gelatinous zooplankton; Salema; Other small pelagic fish; Round sardinella; White seabream; Common two-banded seabream; Poor cod; Seaweeds; Terns; Endangered and pelagic seabirds; Bottlenose dolphins; Striped dolphins; Erected algae; Large phytoplankton; Mediterranean seagrass; Other seagrasses; Small phytoplankton; Red mullet; European lobster; Surmulet; Loggerhead turtles; Red scorpionfish; Scorpaenidae; Small-spotted catshark; Non-commercial large pelagic fishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Central Baltic Sea (1974)}, $\rho = 0.176800$} \\
\hline
Mysids; macrozoobenthos; Detritus-water column; meiozoobenthos; Ad. Sprat; microzooplankton; Cod 0 / Cod 1; Cod 2 / Cod 3; Ad. Cod; Ad. Herring; Herring 0 / Herring 1 / Herring; Sprat 0 / Sprat 1; Cod larvae; Cyanobacteria; other phytoplankton; spring phytoplankton; Acartia sp; other mesozooplankton; Temora sp; Pseudocalanus sp.; Seals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Medes Island MPA (2000)}, $\rho = 0.176483$} \\
\hline
Meso and microzooplankton; Macrozooplankton; Other macro-benthos; Suprabenthos; Other sea urchin; Purple sea urchin; Sea cucumbers; Bivalves; Gastropods; Non-commmercial decapods; Benthopelagic cephalopods; No commercial small demersal fish; Labridae and serranidae; Sparidae; Other commercial decapods; Other medium pelagic fishes; Flatfishes; Mugilidae; Brown meagre; Other corals and gorgonians; Red coral; Coastal benthic cephalopods; Common dentex; Rays and skates; European conger; European hake; Anglerfish; Other commercial medium demersal fish; No commercial medium demersal fish; Horse mackerels; Mackerels; European sardine; Gulls and cormorants; Groupers; Other benthic cephalopods; Torpedos; Common pandora; European anchovy; Jellyfish; Salps and other gelatinous zooplankton; Other small pelagic fish; Round sardinella; Salema; White seabream; Common two-banded seabream; Poor cod; Seaweeds; Terns; Endangered and pelagic seabirds; Striped dolphins; Bottlenose dolphins; Erected algae; Large phytoplankton; Mediterranean seagrass; Other seagrasses; Small phytoplankton; Red mullet; European lobster; Surmulet; Loggerhead turtles; Scorpaenidae; Red scorpionfish; Small-spotted catshark; Non-commercial large pelagic fishes; Other large pelagic fishes\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Aegean Sea (2003)}, $\rho = 0.176198$} \\
\hline
Micro/Mesozooplankton; Macrozooplankton; Benthic invertebrates; Squids; Benthic small crustaceans; Polychaetes; Shrimps; Shelf crabs; Lobsters; Flatfishes; Slope crabs; Seabirds; Norway lobster; Dolphins; European hake; Monk seal; Phytoplankton; Jellyfish; Small demersals 2; European pilchard; European anchovy; Other small pelagics; Medium pelagics; Small demersals 1; Octopus and cuttlefish; Other gadiforms; Picarels and bogue; Mackerels; Sea turtles; Planktivorous deep sea fish; Red mullets; Horse mackerels; Small demersals 3; Gurnards; Piscivorous deep sea fish; Medium-large demersals 2; Rockfish; Rays and skates; Medium-large demersals 1; Anglerfish; Sharks; Large pelagics\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Western Antarctic Peninsula (1996)}, $\rho = 0.175318$} \\
\hline
Benthic invertbrates; Micro-Zool; Meso zooplankton; Krill Small; Krill Large; Other Euphausiids; Macro-zoopl; On-shelf fish; G gibberifrons; Killer whales; Myctophids; Cephalopods; N. rossii; Antarctic fur seals; Salps; Leopard Seal; C gunnari; Ice Algae; Large phytoplankton; Small phytoplankton; Adelie Penguins; Chinstrap Penguins; Minke Whales; Fin Whales; Blue Whales; Humpback whales; Gentoo Penguins; Crabeater Seal; Macaroni Penguins; Emperor Penguins; Flying Birds; Sperm Whales; Weddell Seal; S Elephant Seals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Upper Chesapeake Bay}, $\rho = 0.175268$} \\
\hline
Free Bacteria; Ctenophores; Suspension Feeding Benthos; Bay anchovy; Particle Attached Bacteria; Menhaden; Meroplankton; Mesozooplankton; Hogchoker; Spot; Croaker; Herrings and Shads; White Perch; Deposit Feeding Benthos; Blue Crab; Benthic Bacteria; Meiofauna; Net Phytoplankton; Rotifers; Catfish; Ciliates; Microphytobenthos; SAV; Picoplankton; Heteroflagellates; American Eel; Striped Bass; Weakfish; Bluefish; Chrysaora\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern British Columbia (2000)}, $\rho = 0.174572$} \\
\hline
Carnivorous jellyfish; Epifaunal invertebrates; Forage fish; Infaunal carnivorous invertebrates; Infaunal invertebrate detritivores; Commercial shrimp; Juvenile lingcod; Corals and sponges; Large crabs; Shallowwater benthic fish; Juvenile Pacific cod; Small squid; Squid; Juvenile turbot; Adult picivorous rockfish; Dogfish; Adult sablefish; Adult turbot; Skates; Seals, sea lions; Adult halibut; Juvenile halibut; Adult Pacific cod; Adult lingcod; Phytoplankton; Copepods; Euphausiids; Odontocetae; Eulachon; Small crabs; Adult herring; Juvenile herring; Juvenile pollock; Juvenile sablefish; Seabirds; Macrophytes; Juvenile POP; Mysticetae; Juvenile planktivorous rockfish; Transient salmon; Juvenile flatfish; Adult POP; Juvenile picivorous rockfish; Adult flatfish; Ratfish; Adult planktivorous rockfish; Pollock; Sea Otters; Chinook salmon; Inshore rockfish; Coho salmon\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Aleutian Islands (1963)}, $\rho = 0.174167$} \\
\hline
Small zooplankton; Cephalopods; Benthic inverts; Shrimps; Epiben carnivores; Large pred demersals; Atka mackerel; Adult pollock; Rockfish; Pacific cod; Shark and skates; Arrowtooth; Large zooplankton; Dem S M; Halibut; Shark mammal eater; Transient orca; Macrophytes; Flatfish; Myctophids; Salmon; Sandlance; Juvenile pollock; Small pelagics; Herring; POP; Sablefish; Large pelagics; Phytoplankton; SSL embryo; SSL pups; Sea otters; Baleen whales; Deep L; Birds; Toothed whales; Small mammals; SSL juveniles; SSL Adults\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{West scotland DeepSea (1974)}, $\rho = 0.174007$} \\
\hline
Large zooplankton; Polychaetes; Prawns and shrimp; Other benthic inverts; Echinoderms; Intermediate sharks; Shallow sharks; Kaups arrowtooth eel; Small zooplankton; Gelatinous plankton; Monkfish; Cephalopods; Blue ling; Deep sharks; Large demersals; Mesopelagic fish; Benthopelagic fish; Ling; Blue whiting; Megrim L. whiffiagonis; Skates and rays; Black scabbard fish; Phytoplankton; Greater forkbeard; Chimeras; Coryphanoides S; Bulls eye black cardinalfish; Orange roughy; Bairds smoothhead; Argentine; Coryphanoides L; Cetaceans; Benthic teleosts\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{West Florida Shelf (1985)}, $\rho = 0.173017$} \\
\hline
anthozoans; microbes; mullet; sessile epibenthos; herbivorous zooplankton; meiobenthos; omnivorous zooplankton; small infauna; mobile epifauna; gastropods; ichthyoplankton; carnivorous zooplankton; echinoderms; large crabs; squid; stomatopods; offshore demersal carnivores; jellyfish; reef invertivores; demersal omnivores; bivalves; shrimp; reef planktivores; nearshore demersal carnivores; medium reef omnivores; nearshore small pelagics; sardine herring scad; small reef omnivores; vermilion snapper; reef crustacean eaters; reef carnivores; pelagic piscivores; offshore small pelagics; king mackerel adult; small sharks and rays; other snapper; other SWG; pelagic sharks; coastal piscivores; lionfish juv; gray triggerfish; black sea bass; red porgy; Spanish mackerel adult; red grouper 5+; seabirds; red grouper 0; red snapper 0; macroalgae; phytoplankton; hogfish; red grouper 2; red grouper 1; grey snapper; red grouper 3; goliath grouper; red snapper 1-2; red grouper 4; gag 0; king mackerel juv; red snapper 3+; other DWG; cobia; blueline tilefish; yellowedge grouper; gag 3; scamp; lionfish adult; gag 1; coastal dolphins; gag 2; gag 4; Spanish mackerel juv; golden tilefish; black grouper; gag 5+; greater amberjack; offshore dolphins; large demersal sharks; microphytobenthos; seagrass\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Kaloko Honokohau (2005)}, $\rho = 0.171243$} \\
\hline
Sharks and jacks; Zooplankton; Corals; Benthic Invts; Urchins; Octocoral; Zoo; Detritivores; Herbivores; MIF; Sea birds; Piscivores; Green sea turtles; Turf algae; CCA; Macroalgae; Phytoplankton; Crown of thorns; Corallivores; SIF; Spinner dolphins; Monk seals; Turf algae\_LB; Rays; Hawksbills\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern British Columbia (1950)}, $\rho = 0.169504$} \\
\hline
Carnivorous jellyfish; Epifaunal invertebrates; Forage fish; Infaunal carnivorous invertebrates; Infaunal invertebrate detritivores; Commercial shrimp; Juvenile lingcod; Odontocetae; Corals and sponges; Small squid; Squid; Juvenile Pacific cod; Juvenile turbot; Large crabs; Shallowwater benthic fish; Adult picivorous rockfish; Adult sablefish; Dogfish; Adult turbot; Skates; Adult Pacific cod; Juvenile halibut; Adult lingcod; Adult halibut; Phytoplankton; Copepods; Euphausiids; Seals, sea lions; Eulachon; Adult herring; Small crabs; Juvenile herring; Juvenile pollock; Seabirds; Juvenile sablefish; Juvenile POP; Mysticetae; Juvenile planktivorous rockfish; Adult POP; Juvenile flatfish; Juvenile picivorous rockfish; Adult flatfish; Ratfish; Adult planktivorous rockfish; Pollock; Chinook salmon; Coho salmon; Inshore rockfish; Macrophytes; Transient salmon; Sea Otters\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Yucatan (1987)}, $\rho = 0.165533$} \\
\hline
Annelids; Microcrustacean; Octopus; Shrimps; Zooplankton; Other mollusks; Red grouper; Benthic prod.; Crabs; Sharks; Herrings; Grunts; Snappers; Mojarra; Phytoplankton; Lobsters; Seatrout; Porgies; Jacks; King mackerel\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Prince William Sound (1994)}, $\rho = 0.164979$} \\
\hline
Shal Sm Epibent; Shal sm Infauna; Deep  Epibent; Shal Lg Epibent; Rockfish; Sharks; Shal lg infauna; Deep Lg Infauna; Meiofauna; Deep sm infauna; Deep demersals; Pinnipeds; Transient Orca; Seabirds; Avian Predators; Pollock 1+; Sablefish; Pac. Cod; Halibut; Herbi-Zooplankt; Omni-zooplankto; Near Omni-zoo; Near Herbi-zoo; Salmon Fry 0-12; Porpoise; Adult Salmon; Nshore Demersal; Juv.  Herring; Adult Herring; Sandlance; Eulachon; Pollock 0; Capelin; Jellies; Squid; Baleen Whales; Lingcod; Resident Orca; Macroalgae/gras; Near Phytoplktn; Offshore Phyto.; Invert-eat Bird; Sea otters; Juv. Atooth.; Adult Atooth\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern Californian Current (1990)}, $\rho = 0.164840$} \\
\hline
amphipods; cephalopods; pandalid shp; juv rock; mackerel; infauna; epibenthic; benthic shp; small flat; benthic fish; dungeness; sablefish; tanner crb; halibut; sperm whales; macrourids; lsthorny; shelf rock; carniv-zoops; micro-zoop; small jellies; arrowtooth; salmon; phytoplankton; copepods; euphausiids; orcas; mesopelagics; forage fish; coastal sharks; dogfish; sea lions; toothed whales; lingcod; harbor seals; fur seals; rex; large jellies; juv flat; juv round; hake; ssthorny; gulls; sardine; english; dover; albacore; skates; grey whales; canary; slope rock; POP; juv thorny; widow; yellowtail; baleen whales; black; petrale; murres; shearwaters\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{South Benguela (1600)}, $\rho = 0.161542$} \\
\hline
Microzooplank.; Gelatinous zoo.; Macrobenthos; Benthicdemers; Meiobenthos; SmallM.parad; Snoek; LargeM.capens; Phytoplankton; Mesozooplank.; Macrozooplank.; SmallM.capens; Seals; Apexchond; Pelagicchond; Cephalopods; Pelagicdemers; Ad.hmack.; Otherlargepel; Seabirds; LargeM.parad; Cetaceans; Chubmackerel; Benthicchond; Benth.producers; Sardine; Anchovy; Othersmallpel; Juv.hmack.; Redeye; Mesopelagics\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{South Benguela (1900)}, $\rho = 0.161542$} \\
\hline
Microzooplankto; Gelatinous zoop; Macrobenthos; Benthic-feedi23; Meiobenthos; Small M. parado; Snoek; Large M. capens; Phytoplankton; Mesozooplankton; Macrozooplankto; Small M. capens; Seals; Apex chondricht; Pelagic-feeding; Cephalopods; Pelagic-feedi22; Adult horse mac; Other large pel; Seabirds; Large M. parado; Cetaceans; Chub mackerel; Benthic-feeding; Benthic produce; Sardine; Anchovy; Other small pel; Juvenile horse; Redeye; Mesopelagics\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{South Benguela (1978)}, $\rho = 0.161542$} \\
\hline
Microzooplank.; Gelatinous zoo.; Macrobenthos; Benthicdemers; Meiobenthos; SmallM.parad; Snoek; LargeM.capens; Phytoplankton; Mesozooplank.; Macrozooplank.; SmallM.capens; Seals; Apexchond; Pelagicchond; Cephalopods; Pelagicdemers; Ad.hmack.; Otherlargepel; Seabirds; LargeM.parad; Cetaceans; Chubmackerel; Benthicchond; Benth.producers; Sardine; Anchovy; Othersmallpel; Juv.hmack.; Redeye; Mesopelagics\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{South of Benguela (1960)}, $\rho = 0.161542$} \\
\hline
Microzooplankto; Gelatinous zooz; Macrobenthos; Benthic-feedi23; Meiobenthos; Small M. parado; Snoek; Large M. capens; Phytoplankton; Mesozoozooplank; Macrozoozooplan; Small M. capens; Seals; Apex chondricht; Pelagic-feeding; Cephalopods; Pelagic-feedi22; Adult horse mac; Seabirds; Other large pel; Large M. parado; Cetaceans; Chub mackerel; Benthic-feeding; Benthic produce; Sardine; Anchovy; Other small pel; Juvenile horse; Redeye; Mesopelagics\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern Benguela (1956)}, $\rho = 0.159211$} \\
\hline
Mesozooplankton; Macrobenthos; Cephalopods; Jellyfish adults; Anchovy adults; Sardine adults; A hake; Other demersals; Crabs; Gobies adults; Macrozooplankton; Snoek; Seals; Sharks; Mesopelagics; Other sm pelagics; J hake; Phytoplankton; Juv. h mackerel; Adult h mackerel; Benthic producers; Birds; Monkfish; Anchovy juvs; Gobies juvs; Jellyfish juvs; Sardine juvs; Lobster; Other linefish; Tuna; Marine Mammals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Humboldt Current (1995)}, $\rho = 0.149248$} \\
\hline
Microzooplankton; macrobenthos; horse mackerels; large hake; medium sciaenids; jumbo squid; butter fishes; gelatinous zooplankton; catfish; conger; mesozooplankton; macrozooplankton; anchovy; Diatoms; medium demersal fish; small hake; small demersals; benthic elasmobranchs; other small pelagics; mackerels; medium hake; other cephalopods; Dino and silicoflagellates; pinnipeds; sardine; seabirds; sea robin; mesopelagics; other large pelagics; flatfishes; cetaceans; chondrichtlyans\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Western Channel (1993)}, $\rho = 0.146664$} \\
\hline
Mesozooplankton; deposit feeders; Bivalves; Scallops; Echinoderms; Shrimp and Praw; Crab; suspension feed; Cephalopods; Commercial crab; Cod Juv; Small demersals; Sharks; Microzooplankton; Pollack; Scad; Sprat; Mackerel; Small gadoids; Herring; Pilchard; Whiting Juv; Sandeels; Seals; Cod Ad; Dab; Lobster; Lemon Sole; Dogfish; Hake; Whiting Ad; John Dory; Seabreams; Rays; Seabirds; Primary produce; Plaice Ad; Plaice Juv; Sole Juv; Sole Ad; Whelk; Basking shark; Marozooplankton; Mullet; Gurnards; Bass; Large Flatfish; Large bottom; Monkfishes; Toothed cetaceans\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Western Channel (1973)}, $\rho = 0.146664$} \\
\hline
Mesozooplankton; deposit feeders; Bivalves; scallops; Echinoderms; Shrimp and Praw; Crab; suspension feed; Cephalopods; Commercial crab; Cod Juv; small demersals; Sharks; Microzooplankton; Pollack; Scad; Sprat; Mackerel; small gadoids; Herring; pilchard; Whiting Juv; Sandeels; seals; Cod Ad; Dab; lobster; Flatfish 1; Dogfish; Hake; Whiting Ad; John Dory; Seabreams; Rays; seabirds; Primary produce; Plaice Ad; Plaice Juv; Sole Juv; Sole Ad; Whelk; Basking shark; Marozooplankton; mullet; Gurnards; Bass; Flatfish 2; Large bottom; Monkfishes; toothed mammals\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Santa Pola Bay (2001)}, $\rho = 0.145762$} \\
\hline
Bivalvos; Copepodos planct.; Anfipodos; Misidaceos; Poliquetos; Gastropodos; Crabs; Cefalópodos; Shrimps; Equinodermos; Pomatomus saltarix; Sphyraena sphyraena; Seriola dumerilii; juv. T. mediterraneus; Serranus; juv. T. ovatus; Trachurus mediterraneus; juv Pelag. planct.; S. scrofa; A regius cultiv.; D. labrax cultiv.; Mugilidae; Sardinella aurita; S. aurata cultiv.; S. aurata salvaje; Trachinotus ovatus; Boops boops; Pelágicos planctivoros; Mullus surmeletus; Sparidae; Algas; Fitoplancton; juv. Mugilidae; juv. B. boops; juv Sparidae; Myliobatis aquila; juv S. aurata; G. buccichi; Balistes capriscus\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Chesapeake (1950)}, $\rho = 0.142525$} \\
\hline
Other in/epi fauna; Littoral forage fish; Reef assoc. fish; Atl. croaker; Other suspension feeders; Spot; Non reef assoc. fish; Blue crab YOY; American eel; Other flatfish; Blue crab adult; Black drum; Hard clam; Weakfish Adult; Soft clam; Non-piscivorous seabirds; American shad; Mesozooplankton; Microzooplankton; Oyster 1+; Phytoplankton; Piscivorous birds; Bay anchovy; Menhaden adult; Striped bass migratory; Menhaden 0-1; Striped bass resident; Catfish; Summer flounder; Sandbar shark; Ctenophores; White perch YOY; Benthic algae; SAV; Gizzard shad; Alewife and herring; Other elasmobranchs; White perch adult; Striped bass YOY; Bluefish adult; Sea nettles; Bluefish YOY; Weakfish YOY; Oyster YOY\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Rocky shore, Monterey Bay, California}, $\rho = 0.142209$} \\
\hline
other phytoplankton; Suidasia sp.; Acmaea pella; Tegula funebralis; Acmaea digitalis; Acmaea scabra; Littorina planaxis; Littorina littorea; Diaulota densissima; Cyanoplar dientens; Dynamenella; Lasaea cistula; zooplankton; Mytilus califomianus; Pagurus samuelis; Chthamalus dalli, C. microtretus; Filicrisia franciscana, Musculus; Ptilocercus ; diatoms, blue-green algae; Gigartina; Endocladia muricata; Perinereis monterea; Nereis grubei; Notoplana acticola; Syllis vittata; Nemenopsis gracilis; Syllis spencer; Thais emarginata; Acanthina spirata; Rhombognathus; Tipulidae; Pachygrapsus; Emplectonema gracili; Balanus glandula\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern Humboldt Current (1997)}, $\rho = 0.142045$} \\
\hline
Microzooplankton; macrobenthos; gelatinous zooplankton; horse mackerels; medium sciaenids; catfish; benthic elasmobranchs; conger; small hake; mesozooplankton; macrozooplankton; anchovy; Diatoms; mackerels; medium demersal fish; jumbo squid; chondrichtlyans; small demersals; other small pelagics; sardine; mesopelagics; other cephalopods; sea robin; Dino and silicoflagellates; butter fishes; pinnipeds; medium hake; other large pelagics; seabirds; cetaceans; flatfishes; large hake\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Falkland Islands (1990)}, $\rho = 0.132328$} \\
\hline
benthic crustaceans; small demersal; grenadier; small cephalopods; dogfish; codling; small zoobenthos; large zoobenthos; hagfish; toothfish ad; rays and sharks; krill; Herbivorous zooplank; carnivorous zooplank; seals and sea lions; toothed whales; jellyfish; hoki juv; hoki ad; penguins; large bathydemersal fish; myctophidae; merluccius hubbsi; large cephalopods; merluccius australis; rock cod; pelagic fish; patagonian squid; baleen whales; Phytopl; small bathydemersal fish; flounder; shorebirds; large demersal; southern blue whiting ad; snoek ad; southern blue whiting juv; toothfish juv; illex squid; basking shark; bathypelagic fish; seabirds; snoek juv\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Crystal River Creek - Delta Temp}, $\rho = 0.131519$} \\
\hline
benthic invertebrates; bay anchovy; zooplankton; sheepshead killifish; goldspotted killifish; silverside; moharra; mullet; gulf killifish; microphytes; macrophytes; molly; catfish; longnosed killifish; spot; black drum; red drum; pinfish; stingray; needlefish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Cypress Dry Season}, $\rho = 0.125725$} \\
\hline
Ter. Invertebrates; Aquatic Invertebrates; Mink; Living POC; Living sediment; Vultures; Tadpoles; Crayfish; Apple Snail; Prawn; Black Bear; Opossum; Hogs; Small Fish, herb + omniv; Small Fish, prim. carniv; Snakes; Turtles; Alligators; Other herons; Raccoon; Armadillo; Mice \& Rats; G. Fox; Understory; Hardwoods Leaves; Bobcat; Medium Frogs; Lizards; Small Frogs; Salamanders; Passeriformes onniv.; Passeriformes pred.; Large Fish; Squirrels; Rabbits; Anseriformes; Large Frogs; White-Tailed Deer; Salamander L; Galliformes; Woodpeckers; Hummingbirds; Caprimulgiformes; Bats; Shrews; Otter; Egrets; Great blue heron; Wood stork; Gruiformes; Florida Panther; Owls; Kites \& Hawks; Pelecaniformes; White ibis; Phytoplankton; Float. vegetation; Periphyton/Macroalgae; Macrophytes; Epiphytes; Vine Leaves; Cypress Leaves; Cypress Wood; HW Wood; Roots\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Central Chile (1998)}, $\rho = 0.120181$} \\
\hline
Carrot prawn (a); Carrot prawn (j); Yellow prawn; Chilean hake (j); Chilean hake (a); Copepopds; Phytoplankton; Euphausiids; Sea Lion; Anchovy (a); Anchovy (j); Pilchard (a); Pilchard (j); Rattail fish; Skates; Pacific sand perch; Big-eye flounder; Horse mackerel; Cardinal fish; Black conger\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Cypress Wet Season}, $\rho = 0.118429$} \\
\hline
Terrst. I; White ibis; Aquatic I; Raccoon; Living POC; Living SED; Vultures; Tadpoles; Prawn; Crayfish; Apple Snail; Black Bear; Opossum; Fish HO; Fish PC; Snakes; Alligators; Turtles; G Fox; Mice \& Rats; Understory; Hardwood L; Salamanders; Anseriformes; M Frog; S Frog; Rabbits; Passeriformes onniv.; Lizards; Squirrels; Passeriformes pred.; L Fish; Galliformes; Other Herons; Egrets; Florida Panther; L Frog; White-Tailed Deer; Salam. L; Hogs; Hummingbirds; Woodpeckers; Armadillo; Caprimulgiformes; Bats; Shrews; Bobcat; Otter; Mink; Kites \& Hawks; Owls; Pelecaniformes; GB Heron; Wood stork; Gruiformes; Phytoplankton; Float Veg.; Periphyton; Macrophytes; Epiphytes; Vine L; Cypress L; Cypress W; Hardwood W; Roots\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{British Columbia coast (1950)}, $\rho = 0.118322$} \\
\hline
other benthos; shrimps; misc. small pelagics; misc. small demersals; crabs; echinoderms; bivalves; sablefish ad.; carn. zooplankton; krill; herb. zooplankton; jellies; small squids; arrowtooth ad.; dogfish; sea lions; myctophids; chinook; pollock ad.; herring ad.; herring juv.; pollock juv.; seals; odontocetae; P. halibut ad.; lingcod; pelagic sharks; salmon shark; P. halibut juv.; Pac. hake; large squids; Pac. Ocean perch; macrophytes; phytoplankton; rajidae / ratfish; yellowfin sole; rock sole; flatfish other; mysticetae; birds zooplanktiv; rockfish other; P. cod ad.; P. cod juv.; arrowtooth juv.; sablefish juv.; sockeye; coho; birds pelag pisciv; birds demer pisciv; misc. pred. pelagics; chum; pink\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{East Bass Strait (1994)}, $\rho = 0.112511$} \\
\hline
Squid; Macrobenthos; Cardinal; Megabenthos; Polychaeta; ShMedPredator; ShLPredator; ShSmPredator; ShMedInvertFeeder; SlopeMPredator; Pelagic sharks; Primary producers; Sm zooplankton; Mesopelagics; Toothed whale; L zooplankton; Gelatinous nekton; Euphausids; Demersal sharks; PelagicPrawns; Redfish; SlopeLPredator; Seal; ShSmInvertFeeder; SlopeSmPredator; Flathead; PelSmInvertFeeder; SlopeSmInvertFeeder; Cucumberfish; Redbait; SlopeMInverFeeder; Blue grenadier; Jack mackerel; SlopeLInvertFeeder; Warehous; Whiting; SlopeOceanPerch; Seabirds; PelMInvertFeeder; ShLInvertFeeder; Rays; PelMPredator; Benthic producer; PelLInvertFeeder; Jackass morwong; Oreos; Baleen whale; Deepsea Cod; Blue-eye trevalla; PelLPredator; Chinaman leatherjacket; ShOceanPerch; Penguins; Ling; Tuna/billfish; Dories; Gemfish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Charca de Maspalomas}, $\rho = 0.112245$} \\
\hline
Benthic Deposit Feeders; Benthic Microfauna; Liza Aurata; Dicentratus punctatus; Pelagic Bacteria; Microzooplankton; Mesozooplankton; Diplodus Sargus; Cyanobacteria; Eukaryotic Phyto; Gallinula chloropus; Benthic Suspension Feeder; Macrozooplankton; Chara globularis; Ruppia Maritima; Cladophora; Periphyton; Benthic Invertebrate Car.\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{North East Pacific (1950)}, $\rho = 0.111416$} \\
\hline
other benthos; shrimps; misc. small pelagics; misc. small demersals; crabs; echinoderms; bivalves; sablefish ad.; carn. zooplankton; krill; herb. zooplankton; jellies; small squids; arrowtooth ad.; odontocetae; sea lions; salmon shark; myctophids; seals; lingcod; pollock juv.; dogfish; P. halibut ad.; pelagic sharks; herring ad.; herring juv.; P. halibut juv.; Pac. hake; Pac. Ocean perch; P. cod ad.; large squids; pollock ad.; rockfish other; macrophytes; phytoplankton; northern rockfish; plaice; rajidae / ratfish; yellowfin sole; rock sole; flatfish other; mysticetae; birds zooplanktiv; atka mackerel; P. cod juv.; arrowtooth juv.; sablefish juv.; sockeye; chinook; coho; birds pelag pisciv; birds demer pisciv; misc. pred. pelagics; chum; pink\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Strait of Georgia (1950)}, $\rho = 0.106097$} \\
\hline
other benthos; crabs; misc. small demersals; shrimps; bivalves; echinoderms; sablefish ad.; carn. zooplankton; krill; herb. zooplankton; jellies; herring ad.; misc. small pelagics; small squids; pollock ad.; dogfish; myctophids; herring juv.; flatfish other; sea lions; arrowtooth ad.; odontocetae; seals; P. halibut ad.; pelagic sharks; salmon shark; lingcod; P. halibut juv.; pollock juv.; Pac. hake; birds pelag pisciv; rockfish other; large squids; macrophytes; phytoplankton; rajidae / ratfish; yellowfin sole; Pac. Ocean perch; rock sole; mysticetae; birds zooplanktiv; P. cod ad.; P. cod juv.; arrowtooth juv.; sablefish juv.; chinook ad.; coho ad.; sockeye; birds demer pisciv; misc. pred. pelagics; chum; coho juv.; pink; chinook juv.\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Northern Californian Current (1960)}, $\rho = 0.105776$} \\
\hline
zooplankton; forage fish and mesopels; benthic invertebrates; shrimps; cephalopods; abalone adult; abalone juvenile; benthic fish; hake; jellyfish; flatfish; sardine; crabs; widow rockfish juvenile; cabezon juvenile; Phytoplankton; cabezon larvae; lingcod larvae; nearshore rockfish larvae; shortbelly rockfish larvae; widow rockfish larvae; lingcod juvenile; mackarel; widow rockfish adult; nearshore rockfish adult; nearshore rockfish juvenile; cabezon adult; shortbelly rockfish juvenile; shortbelly rockfish adult; salmon; dogfish; sablefish; seals and sealions; lingcod adult; Macroalgae\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Arctic seas}, $\rho = 0.102912$} \\
\hline
phytoplankton; benthonic invertebrates; bacteria; larger zooplankton; Greenland shark; killer whale; caplin; smaller zooplankton; benthoni vertebrates; narwhal; walrus; bearded seals; beluga; right whales; clupeid fishes; rorquals; artic char; ringed seal; cod; harp seal; harbour seal\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Shallow sublittoral, Cape Ann, Massachusetts}, $\rho = 0.099548$} \\
\hline
annelids; Myoxocephalus; Pomatomus, Poronatus; isopods, Gammarus, Caprella; Crago; Pagurus, Cancer; plankton and detritus; Polinices; Fundulus, fish fry; macroalgae; Mytilus, Gemma; Scomber, Qupea; Loligo; Chalina; Abietinaria, Sertularia, Metridium; Lichenophora; Littorina littorea; Strongylocentrotus; Limulus; Raja; Asterias; Phoca; Sterna\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Ythan estuary, Aberdeenshire, Scotland}, $\rho = 0.096430$} \\
\hline
Flounder Platichthyes fiesus; Corophium volutator; Ragworm Nereis diversicolor; Barnacles Semibalanus balanoides; Gammurus sp.; Hydrobia ulvae; Macoma balthica; Mytilus edulis; Cerastoderma edule; Nematodes; Brown shrimp Crangon crangon; Ostracods; Brown shrimp Crangon crangon; Oppossum shrimp Neomysis integer; Formaifera; Butterfish Pholis gunnellus; Viviparous blenny Zoarces viviparous; Fatherlasher Myxocephalus scorpius; Calanoid copepods; Harpacticoid copepods; Sand goby Pomatoschistus minutus; Sandeel Ammodytes tobianus; Common goby Pomatoschistus microps; Jaera albifrons; Talitrus saltator; Bathyporeia pilosa; Idotea emariginata; Eurydice pulchra; Nototropis sp.; Pygospio elegans; Manayunkia aestuarina; Parathemisto sp.; Capitella capitata; Arenicola marina; Chironomidae; Aricia sp.; Mya arenaria; Dipteran larvae; Acarina; Hesionidae; King ragworm Nereis virens; Phyllodoce mucosa; Littorina littorea; Herring Clupea harengus; Spratt Sprattus sprattus; Eel Anguilla anguilla; Podocotyle staffordi; Redshank Tringa totanus; Saithe Pollachius virens; Common gull Larus canus; Herring gull Larus argentatus; Enteromorpha; Oystercatcher Haematopus ostralegus; Catatropis verrucosa; Black headed gull Larus ridibundus; Levinseniella brachysoma; Amidostomum sp.; Five bearded rockling Ciliata mustella; Maritrema gratiosum; Trout Salmo trutta; Hysterothylacium aduncum; Spelotrema claviforma; Cryptocotyle lingua; Himasthla elongata; Profilicollis botulus; Haploparaksis crassirostris; Littorina saxatilis; Renicola roscovita; Maritrema subdolum; Levinseniella sp. no.17; Psilostomum brevicolle; Eteone longa; Hymenolepis sp. 1; Cercariae lebouri; Cryptocotyle jejuna; Himasthla continua; Maritrema oocysta; Microphallid sp. no.15; Notocotyledae sp. no.14; Himasthla interrupt; Ophryocotyle insignis; Parvatrema affine; Apophallus lerouxi; Maritrema humile; Tubificoides benedini; Tubifex costatus; Phytoplankton; Brown algae; Mute swan Cygnus olor; Wigeon Anas penelope; Hyale nilssoni; Alderia modesta; Eider Somateria mollissima; Shelduck Tadorna tadorna; Echinorynchus gadi; Turnstone Arenaria interpres; Retusa obtusa; Lapwing Vanellus vanellus; Eider juvenile; Three-spined stickleback Gasterosteus aculeatus; Flounder juvenile; Plaice juvenile Pleuronectes platessa; Rook Corvus frugilegus; Crow Corvus corone; Nilsson's pipefish Sygnathus rostellatus; Ringed plover Charadris hiaticula; Golden plover Pluvialis apricaria; Grey plover Pluvialis squatarola; Dunlin Calidris alpina; Curlew Numenius arquata; Pogge Agonus cataphractus; Cormorant Phalacrocorax carbo; Great black-backed gull Larus marinus; Lacunovermis macomae; Cucullanus minutus; Pomphorynchus sp.; Corynosoma strumosum; Cestode sp.1; Lecithaster gibbosus; Tetraphyllidean larvae; Heron Ardea cinerea; Cucullanus heterochrous; Derogenes varicus; Hemiuris communis; Bar-tailed godwit Limosa lapponica; Opacelididii sp.; Otter Lutra lutra; Anisakis sp.; Zoogonoides viviparus; Spiruroid larvae; Sandwich tern Sterna sandvicensis; Common tern Sterna hirundo; Arctic tern Sterna paradise\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Little Rock Lake, Wisconsin}, $\rho = 0.092640$} \\
\hline
Alona affinis; Alona quadrangularis; Alona rustica; Alona intermedia; Alonella excisa; Disparalona acutirostris; Chydorus sp1; Chydorus sp2; Acantholeberis curvirostris; Ophryoxus gracilis; Scapholeberis kingi; Sida crystallina; Tanytarsus; Oligochaete; Cyclopoid *copepodids; Harpacticoid copepods; Harpacticoid copepodids; Sphaeromais; Leptophlebia; Caenis; Limnephilus; Polycentropus; Chaetocladius; Corynoneura; Cricotopus; Nanocladius; Micropsectra; Paratanytarsus; Chironomus; Cladopelma; Endochironomus; Glyptotendipes; Microtendipes; Paratendipes; Pseudochironomus; Stenochironomus; Stictochironomus; Bivalvia; Campeloma decisum; Sphaeriidae; Spongilla lacustris; Ephydatia muelleri; Corvomyenia everetti; Epischura lacustris; Parachironomus; Polypedilum; Crangonyx gracilis; Hirudinea; Gyrinus; Largemouth bass (Micropterus salmoides); Largemouth bass (Micropterus salmoides); Leptodora kindtii; Polyphemus pediculus; Mudminnow (Umbra); Black crappie (Pomoxis nigromaculatus); Yellow perch (Perca flavescens); Rock bass (Ambloplites rupestris),; Rock bass (Ambloplites rupestris); Yellow perch (Perca flavescens); Black crappie (Pomoxis nigromaculatus); Asplanchna; Shiner (Notemigonus crysoleucus); Tropocyclops prasinus; Cryptochironomus; Diaptomus *bithomasi; Mesocyclops edax; Diaptomus minutus; Gerris; Veliidae; Notonectids; Daphnia galeata mendotae; Daphnia parvula; Diaphanosoma birgei; Holopedium gibberum; Ablabesmyia; *Djalmabatista; Guttipelopia; Bosmina longirostris; Eubosmina; Larsia; Chroococcus; Merismopedia; Gomphosphaeria; Rhabdoderma; Aphanothece; Crucigenia; Euastrum; O”cystis; Schroederia; Tetra‰dron; Ankistrodesmus; Elaktothrix; Scenedesmus; Chroomonas; Cryptomonas; Clinotanypus; Macropelopis; Procladius; Eucyclops serrulatus; Acanthocyclops; Xenochironomus; Chaoborus *albatus; Chaoborus *punctipennis; Bezzia; Macrocyclops albidus; Microcyclops rubellus; LEPIDOPTERA Pyralidae eoparagyractis; Fish eggs; Hydroporus; Bambusina; Batrachospermum; Binuclearia; Bulbochaete; Desmidium; Geminella; *Greonbladia; Hapalosiphon; Hyalotheca; Lyngbya; Microchaete; Microcoleus; Mougeotia; Oedogonium; Oscillatoria; Phormidium; Plectonema; Radiofilum; Rhizoclonium; Schizothrix; Scytonema; Sphaerozosma; Spirogyra; Tribonema; Zygnema; Gloeothece; Aphanocapsa; Coelosphaerium; Anabaena; Arthrodesmus; Cosmarium; Pediastrum; Quadrigula; Spondylosium; Staurastrum; Xanthidium; Phacus; Trachelomonas; Asterionella; Dinobryon; Mallomonas; Synedra; Synura; Tabellaria; Conochilus unicornis; Conochiloides; Kellicottia longispina; Kellicottia bostoniensis; Keratella cochlearis; Keratella taurocephala; Keratella crassa; Keratella hiemalis; Polyarthra remata; Polyarthra vulgaris; Trichocerca cylindrica; Gastropus; Synchaeta; Nauplii; Calanoid *copepodids; Oecetis; Mystacides; Agrypnia; Climacia; Tricladida; Enallagma; Anisoptera epitheca; Libellula; Sympetrum; Hydracarina; Banksiola; Molanna; Sialis\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Tasek Bera swamp, Malaysia}, $\rho = 0.081756$} \\
\hline
bacteria, fungi; detriuvorous invertebrates; detritivorous fishes; carnivorous fishes; emergent herbivorous insects; benthic carnivores; snakes; invertebrate defoliators; benthic herbivores; emergent carnivorous insects; periphyton; submerged macrophytes; vertebrate herbivores; spiders; phytoplankton; Utricularia; Pandanus; swamp forest; zooplankton; herbivorous fishes; shrimps; carnivorous invertebrates; frogs; swallows; Martin pescatore\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Swamp, south Florida}, $\rho = 0.074074$} \\
\hline
insect larvae; crayfish; plecopterans, odonates, hemipterans; cyprinodontids; amphipods; bobcats; snakes, turtles; centrarchids; dipterans; alligators; phytoplankton, periphyton; vascular plants; coleopterans; pickerel; copepods; coadocerans; waterfowl, marsh rabbits, deer, water rat; mosquitofish; hemipterans; raccoons; bowfin; gar; opossum; Accipitridae; egrets; herons, ibises\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Chesapeake Bay Mesohaline}, $\rho = 0.063669$} \\
\hline
bacteria in sediment poc; zooplankton; blue crab; bay anchovy; menhaden; ctenophores; free bacteria; mya arenaria; bacteria in suspended poc; ciliates; spot; phytoplankton; other polychaetes; nereis; crustacean deposit feeder; oysters; other suspension feeders; benthic diatoms; heterotrophic microflagel; alewife \& blue herring; sea nettle; weakfish; meiofauna; macoma spp.; fish larvae; shad; striped bass; hogchoker; white perch; summer flounder; croaker; catfish; bluefish\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{St. Marks River (Florida)}, $\rho = 0.061475$} \\
\hline
Benthic bact; Bacterio plankton; Micro protozoa; Predatory polycht; Predatory gastropod; Benthic algae; Omnivorous crabs; Zooplankton; Microfauna; Micro-epiphytes; Halodule; Predatory shrimp; Meiofauna; Spot; Pinfish; Atl. silverside \& bay anc; Benthos-eating birds; suspension-feed molluscs; Sheepshead minnow; Herbivorous shrimp; Epiphyte-graz amphipods; Hermit crab; Deposit feed amphipods; Macro-epiphytes; Deposit-feed polycht; Phytoplankton; Isopod; Spider crab; Killifish; Gulf flound \& needle fish; Deposit-feed gastropod; Blue crab; Gobies \& blennies; Southrn hake \& sea robins; Catfish \& stingrays; Epiphyte-graz gastropod; Other gastropods; Suspension-feed polychts; Detritus feed crust.; Brittle stars; Tongue fish; Pipefish \& seahorses; Red Drum; Herbivorous ducks; Gulls; Fish \& crust. eating bird; Fish-eating birds; Raptors\\
\fullhline
\hline
\multicolumn{1}{|c|}{\textbf{Salt meadow, New Zealand}, $\rho = 0.043401$} \\
\hline
amphipods; collembola; mites; fungi; harpacticoids; staphylinids; dipterous larvae; haplotaxid worms; oribatids; leaves; Dotterel; roots; phytophagus nematodes; rabbits; flowers; rotifers; parasitic hymenopterous larvae; seeds; algae; bacteria; weevil larvae; coccids; lepidopterus larvae; other hemiptera; Uromyces scaevolae; bumblebees; adult hymenopterans; tartigrades; Trichostrongylus retortaeformis; Graphidium strigosum; Passalurus ambiguus; stoats; ants; carnivorous namatodes; trombidiform mites; spiders; Hymenolepididae; nematode; analgesid mites; other mites; lice; redpolls; starlings; harrier hawks\\
\fullhline